---
title: "compare_xls_figures_vs_present_model_input"
author: "Kirsten Birch Håkansson, DTU Aqua"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = F, message = F, out.width = "150%",
                      out.height = "200%")
library(dplyr)
library(ggplot2)

library(RColorBrewer)
library(knitr)

path_model_input <- "./boot/data/download_from_stockassessment_org_multi_fleet/"
path_data <- "./data/"
```

Here I compare the data from the old spreadsheets, 2000-2015, with the data in the present model.

CANUM from the old spreadsheet is splitted with the old split

So CANUM, WECA and split from the spreadsheets

**Summary**

It looks close to perfect in 3a, but in 22-24 there are some minor differences. In Tomas notes I can see that some of these are due to updates, but I have not been able to find the updated spreadsheets.


# Get data
```{r, include = T}
# Model ----
cn <- c()

for (i in c("A", "C", "D", "F")) {
  cn_0 <- read.csv(paste0(path_model_input, "cn_", i, ".dat"),
                   sep = "",
                   header = F)
  year_min <- as.numeric(cn_0[3, 1])
  year_max <- as.numeric(cn_0[3, 2])
  cn_0_dat <- cn_0[c(6:((year_max - year_min) + 6)), c(1:9)]
  names(cn_0_dat) <- c("wr0", "wr1", "wr2", "wr3", "wr4", "wr5", "wr6", "wr7", "wr8+")
  cn_0_dat$year <- c(year_min:year_max)
  cn_0_dat$fleet <- i
  
  cn <- rbind(cn, cn_0_dat)
  
}

cn_t <- tidyr::gather(cn, key = "wr", value = "canum_1000_model", -year, -fleet)
cn_t$wr <- gsub("wr", "", cn_t$wr)
cn_t$canum_1000_model <- as.numeric(cn_t$canum_1000_model)
cn_t$stock <- "wbss"

cw <- c()

for (i in c("A", "C", "D", "F")) {
  cw_0 <- read.csv(paste0(path_model_input, "cw_", i, ".dat"),
                   sep = "",
                   header = F)
  year_min <- as.numeric(cw_0[3, 1])
  year_max <- as.numeric(cw_0[3, 2])
  cw_0_dat <- cw_0[c(6:((year_max - year_min) + 6)), c(1:9)]
  names(cw_0_dat) <- c("wr0", "wr1", "wr2", "wr3", "wr4", "wr5", "wr6", "wr7", "wr8+")
  cw_0_dat$year <- c(year_min:year_max)
  cw_0_dat$fleet <- i
  
  cw <- rbind(cw, cw_0_dat)
  
}

cw_t <- tidyr::gather(cw, key = "wr", value = "weca_kg_model", -year, -fleet)
cw_t$wr <- gsub("wr", "", cw_t$wr)
cw_t$weca_kg_model <- as.numeric(cw_t$weca_kg_model)
cw_t$weca_g_model <- cw_t$weca_kg_model * 1000
cw_t$stock <- "wbss"

```

```{r, include = T}

dat_old <- read.csv(paste0(path_data, "01_old_canum_with_imputations_2000_2015_IIIa.csv") ,sep = ";")

# Test 
dat_old_miss <- subset(dat_old, catch_t > 0 & canum %in% c(NA, 0))

sop <- summarise(group_by(dat_old, ctry, year, area, 
              quarter, fleet, catch_t),
              sop = sum((canum_1000 * weca_g) / 1000, na.rm = T))


dat_old_sop <- left_join(dat_old, sop)
dat_old_sop$sopCorr <- (dat_old_sop$catch_t / dat_old_sop$sop)

nrow(subset(dat_old_sop, sopCorr != 1 & catch_t == 0))
check_sop <- subset(dat_old_sop, sopCorr != 1 & catch_t == 0)

dat_sum <- summarise(group_by(dat_old, year, area, quarter, fleet, wr),
                     weca_g = sum(weca_g * canum_1000, na.rm = T) /
                        sum(canum_1000, na.rm = T),
                     canum_1000 = sum(canum_1000, na.rm = T))


split <- read.csv(paste0(path_data, "04_old_split_2000_2015_SD20SD21.csv") ,sep = ";")

splitted <- left_join(dat_sum, split)

# WBSS
wbss <- splitted
wbss$canum_1000 <- wbss$canum_1000 * wbss$wbss
# wbss$caton <- wbss$canum_1000 * wbss$weca_g / 1000

wbss <- summarise(group_by(wbss, year, fleet, wr),
                     weca_g = sum(weca_g * canum_1000, na.rm = T) /
                        sum(canum_1000, na.rm = T),
                     canum_1000 = sum(canum_1000 , na.rm = T))

# wbss$weca_g <- (wbss$caton * 1000 / wbss$canum_1000)
wbss$stock <- "wbss"

# NSAS
nsas <- splitted
nsas$canum_1000 <- nsas$canum_1000 * nsas$nsas
nsas$caton <- nsas$canum_1000 * nsas$weca_g / 1000

nsas <-
  aggregate(
    cbind(canum_1000, caton) ~ year + wr + fleet,
    data = nsas,
    FUN = sum, na.rm = T
  )

nsas$weca_g <- (nsas$caton * 1000 / nsas$canum_1000)
nsas$stock <- "nsas"


dat_2224 <- read.csv(paste0(path_data, "02_old_canum_with_imputations_2000_2015_22-24.csv") ,sep = ";")
wbss_2224 <- summarise(group_by(dat_2224, year, fleet, wr),
                     weca_g = sum(weca_g * canum_1000, na.rm = T) /
                        sum(canum_1000, na.rm = T),
                     canum_1000 = sum(canum_1000 , na.rm = T))

wbss_2224$fleet <- "F"
wbss_2224$stock <- "wbss"
wbss <- bind_rows(wbss, wbss_2224)
wbss <- subset(wbss, fleet != "E")
```

```{r, include = T}
comb_w <- left_join(cw_t, wbss)
comb_w_1 <- left_join(comb_w, cn_t)
comb_w_1$canum_1000[is.na(comb_w_1$canum_1000)] <- 0
comb_w_1$canum_1000_model[is.na(comb_w_1$canum_1000_model)] <- 0
# comb_w_1$weca_g_model[comb_w_1$canum_1000_model == 0] <- 0
# comb_w_1$weca_g[comb_w_1$canum_1000 == 0] <- 0
comb_w_1$canum_diff_no <- round(comb_w_1$canum_1000_model - comb_w_1$canum_1000, digits = 0)
comb_w_1$weca_diff_g <- round(comb_w_1$weca_g_model - comb_w_1$weca_g, digits = 0)
comb_w_1 <- select(comb_w_1, -weca_kg_model)
comb_w_1 <- arrange(comb_w_1, year, fleet, wr)

model <- left_join(cn_t, cw_t)
model <- rename(model, canum_1000 = canum_1000_model, weca_g = weca_g_model)
model$type <- "present model input"
wbss$type <- "figures from xsl"

comb_l <- bind_rows(model, wbss)
 # comb_l$weca_g[comb_l$canum_1000 == 0] <- NA
```

# Compare canum

```{r}

ggplot(data = comb_l, aes(x = year, y = canum_1000, col = type)) +
  geom_line() +
  scale_color_brewer(palette = "Dark2") +
  facet_grid(wr~fleet, scales = "free_y") +
    theme(legend.position="bottom")

```

```{r}
kable(subset(comb_w_1, canum_diff_no != 0 & year < 2016 & !(fleet %in% c("A"))), caption = "Differences")

subset(comb_w_1, is.na(canum_1000) & !(is.na(canum_1000_model)) & year < 2016 & !(fleet %in% c("A")))
subset(comb_w_1, is.na(canum_1000_model) & !(is.na(canum_1000)) & year < 2016 & !(fleet %in% c("A")))

```


# Compare weca

```{r}
comb_l$weca_g[comb_l$canum_1000 == 0] <- NA
ggplot(data = comb_l, aes(x = year, y = weca_g, col = type)) +
  geom_line() +
  scale_color_brewer(palette = "Dark2") +
  facet_grid(wr~fleet, scales = "free_y") + expand_limits(y = 0) +
    theme(legend.position="bottom")

```

```{r}
kable(subset(comb_w_1, weca_diff_g != 0 & year < 2016 & !(fleet %in% c("A"))), caption = "Differences")

subset(comb_w_1, is.na(weca_g) & !(is.na(weca_g_model)) & year < 2016 & !(fleet %in% c("A")))
subset(comb_w_1, is.na(weca_g_model) & !(is.na(weca_g)) & year < 2016 & !(fleet %in% c("A")))
```


