---
title: "read_in"
author: "Kirsten Birch Håkansson, DTU Aqua"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = F, message = F)

library(readxl)
library(dplyr)

source("./utils/read_canum_sheet_old_format_IIIa.R")

path_in <- "./boot/data/historical_data/sc_sheets_old_format/"

```

# 2000
Total CATON and CANUM checked against Thomas figures: 
Total CATON and CANUM checked against report:
Total CATON and CANUM checked against spread sheet: 
Imputations checked against spread sheet: 
```{r, eval = F}
file <- "HER-IIIa-2005_ok.xls" 
# Fleet E and not fleet D is used - 
#  in the summary and report it looks like E become D, so this will be corrected in the end

sheet_names <- excel_sheets(path = paste0(path_in, file))

SD20SE <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD20-SE") 
sum(unique(SD20SE$catch_t))
SD20SE$imputation <- NA
SD20SE$imputation[SD20SE$quarter == 3 & SD20SE$fleet == "E"] <- "DK, E, Q3, 20"

SD20DK <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD20-DK")
sum(unique(SD20DK$catch_t))
SD20DK$imputation <- NA
SD20DK$imputation[SD20DK$quarter == 1 & SD20DK$fleet == "C"] <- "SE, C, Q1, 20"
SD20DK$imputation[SD20DK$quarter == 2 & SD20DK$fleet == "C"] <- "SE, C, Q2, 20"
SD20DK$imputation[SD20DK$quarter == 1 & SD20DK$fleet == "E"] <- "SE, E, Q1, 20"

SD20DE <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD20-OTH")
sum(unique(SD20DE$catch_t))
SD20DE$imputation <- NA
SD20DE$imputation[SD20DE$quarter == 3 & SD20DE$fleet == "C"] <- "DK, C, Q3, 20"
SD20DE$imputation[SD20DE$quarter == 4 & SD20DE$fleet == "C"] <- "DK, C, Q4, 20"

SD20FO <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD20-OTH (2)")
sum(unique(SD20FO$catch_t))
SD20FO$imputation <- NA
SD20FO$imputation[SD20FO$quarter == 3 & SD20FO$fleet == "E"] <- "DK, E, Q3, 20"
SD20FO$imputation[SD20FO$quarter == 4 & SD20FO$fleet == "E"] <- "DK, E, Q4, 20"

SD21SE <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD21-SE")
sum(unique(SD21SE$catch_t))
SD21SE$imputation <- NA
SD21SE$imputation <- NA
SD21SE$imputation[SD21SE$quarter == 1 & SD21SE$fleet == "E"] <- "DK, C, Q1, 21"
SD21SE$imputation[SD21SE$quarter == 3 & SD21SE$fleet == "E"] <- "DK, C, Q2, 21"
SD21SE$imputation[SD21SE$quarter == 4 & SD21SE$fleet == "E"] <- "DK, C, Q3, 21"

SD21DK <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD21-DK")
sum(unique(SD21DK$catch_t))
SD21DK$imputation <- NA
SD21DK$imputation[SD21DK$quarter == 2 & SD21DK$fleet == "C"] <- "SE, C, Q2, 21"
SD21DK$imputation[SD21DK$quarter == 3 & SD21DK$fleet == "C"] <- "SE, C, Q3, 21"


c05 <- bind_rows(SD20DE, SD20DK, SD20FO, SD20SE, SD21DK, SD21SE)

# Rename fleet E to D
c05 <- subset(c05, fleet != "D")
c05$fleet[c05$fleet == "E"] <- "D"

rm(SD20DE, SD20DK, SD20FO, SD20SE, SD21DK, SD21SE)

summarise(group_by(subset(c05, wr == "8+"), year, division), ton = sum(catch_t, na.rm = T))
summarise(group_by(c05, year, division), canum = sum(canum, na.rm = T))

```

# 2001
Total CATON and CANUM checked against Thomas figures: 
Total CATON and CANUM checked against report:
Total CATON and CANUM checked against spread sheet: 
Imputations checked against spread sheet: 
```{r, eval = F}
file <- "HER-IIIa-2005_ok.xls" 
# Fleet E and not fleet D is used - 
#  in the summary and report it looks like E become D, so this will be corrected in the end

sheet_names <- excel_sheets(path = paste0(path_in, file))

SD20SE <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD20-SE") 
sum(unique(SD20SE$catch_t))
SD20SE$imputation <- NA
SD20SE$imputation[SD20SE$quarter == 3 & SD20SE$fleet == "E"] <- "DK, E, Q3, 20"

SD20DK <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD20-DK")
sum(unique(SD20DK$catch_t))
SD20DK$imputation <- NA
SD20DK$imputation[SD20DK$quarter == 1 & SD20DK$fleet == "C"] <- "SE, C, Q1, 20"
SD20DK$imputation[SD20DK$quarter == 2 & SD20DK$fleet == "C"] <- "SE, C, Q2, 20"
SD20DK$imputation[SD20DK$quarter == 1 & SD20DK$fleet == "E"] <- "SE, E, Q1, 20"

SD20DE <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD20-OTH")
sum(unique(SD20DE$catch_t))
SD20DE$imputation <- NA
SD20DE$imputation[SD20DE$quarter == 3 & SD20DE$fleet == "C"] <- "DK, C, Q3, 20"
SD20DE$imputation[SD20DE$quarter == 4 & SD20DE$fleet == "C"] <- "DK, C, Q4, 20"

SD20FO <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD20-OTH (2)")
sum(unique(SD20FO$catch_t))
SD20FO$imputation <- NA
SD20FO$imputation[SD20FO$quarter == 3 & SD20FO$fleet == "E"] <- "DK, E, Q3, 20"
SD20FO$imputation[SD20FO$quarter == 4 & SD20FO$fleet == "E"] <- "DK, E, Q4, 20"

SD21SE <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD21-SE")
sum(unique(SD21SE$catch_t))
SD21SE$imputation <- NA
SD21SE$imputation <- NA
SD21SE$imputation[SD21SE$quarter == 1 & SD21SE$fleet == "E"] <- "DK, C, Q1, 21"
SD21SE$imputation[SD21SE$quarter == 3 & SD21SE$fleet == "E"] <- "DK, C, Q2, 21"
SD21SE$imputation[SD21SE$quarter == 4 & SD21SE$fleet == "E"] <- "DK, C, Q3, 21"

SD21DK <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD21-DK")
sum(unique(SD21DK$catch_t))
SD21DK$imputation <- NA
SD21DK$imputation[SD21DK$quarter == 2 & SD21DK$fleet == "C"] <- "SE, C, Q2, 21"
SD21DK$imputation[SD21DK$quarter == 3 & SD21DK$fleet == "C"] <- "SE, C, Q3, 21"


c05 <- bind_rows(SD20DE, SD20DK, SD20FO, SD20SE, SD21DK, SD21SE)

# Rename fleet E to D
c05 <- subset(c05, fleet != "D")
c05$fleet[c05$fleet == "E"] <- "D"

rm(SD20DE, SD20DK, SD20FO, SD20SE, SD21DK, SD21SE)

summarise(group_by(subset(c05, wr == "8+"), year, division), ton = sum(catch_t, na.rm = T))
summarise(group_by(c05, year, division), canum = sum(canum, na.rm = T))

```

# 2002
Total CATON and CANUM checked against Thomas figures: 
Total CATON and CANUM checked against report:
Total CATON and CANUM checked against spread sheet: 
Imputations checked against spread sheet: 
```{r, eval = F}
file <- "HER-IIIa-2005_ok.xls" 
# Fleet E and not fleet D is used - 
#  in the summary and report it looks like E become D, so this will be corrected in the end

sheet_names <- excel_sheets(path = paste0(path_in, file))

SD20SE <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD20-SE") 
sum(unique(SD20SE$catch_t))
SD20SE$imputation <- NA
SD20SE$imputation[SD20SE$quarter == 3 & SD20SE$fleet == "E"] <- "DK, E, Q3, 20"

SD20DK <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD20-DK")
sum(unique(SD20DK$catch_t))
SD20DK$imputation <- NA
SD20DK$imputation[SD20DK$quarter == 1 & SD20DK$fleet == "C"] <- "SE, C, Q1, 20"
SD20DK$imputation[SD20DK$quarter == 2 & SD20DK$fleet == "C"] <- "SE, C, Q2, 20"
SD20DK$imputation[SD20DK$quarter == 1 & SD20DK$fleet == "E"] <- "SE, E, Q1, 20"

SD20DE <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD20-OTH")
sum(unique(SD20DE$catch_t))
SD20DE$imputation <- NA
SD20DE$imputation[SD20DE$quarter == 3 & SD20DE$fleet == "C"] <- "DK, C, Q3, 20"
SD20DE$imputation[SD20DE$quarter == 4 & SD20DE$fleet == "C"] <- "DK, C, Q4, 20"

SD20FO <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD20-OTH (2)")
sum(unique(SD20FO$catch_t))
SD20FO$imputation <- NA
SD20FO$imputation[SD20FO$quarter == 3 & SD20FO$fleet == "E"] <- "DK, E, Q3, 20"
SD20FO$imputation[SD20FO$quarter == 4 & SD20FO$fleet == "E"] <- "DK, E, Q4, 20"

SD21SE <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD21-SE")
sum(unique(SD21SE$catch_t))
SD21SE$imputation <- NA
SD21SE$imputation <- NA
SD21SE$imputation[SD21SE$quarter == 1 & SD21SE$fleet == "E"] <- "DK, C, Q1, 21"
SD21SE$imputation[SD21SE$quarter == 3 & SD21SE$fleet == "E"] <- "DK, C, Q2, 21"
SD21SE$imputation[SD21SE$quarter == 4 & SD21SE$fleet == "E"] <- "DK, C, Q3, 21"

SD21DK <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD21-DK")
sum(unique(SD21DK$catch_t))
SD21DK$imputation <- NA
SD21DK$imputation[SD21DK$quarter == 2 & SD21DK$fleet == "C"] <- "SE, C, Q2, 21"
SD21DK$imputation[SD21DK$quarter == 3 & SD21DK$fleet == "C"] <- "SE, C, Q3, 21"


c05 <- bind_rows(SD20DE, SD20DK, SD20FO, SD20SE, SD21DK, SD21SE)

# Rename fleet E to D
c05 <- subset(c05, fleet != "D")
c05$fleet[c05$fleet == "E"] <- "D"

rm(SD20DE, SD20DK, SD20FO, SD20SE, SD21DK, SD21SE)

summarise(group_by(subset(c05, wr == "8+"), year, division), ton = sum(catch_t, na.rm = T))
summarise(group_by(c05, year, division), canum = sum(canum, na.rm = T))

```

# 2003
Total CATON and CANUM checked against Thomas figures: 
Total CATON and CANUM checked against report:
Total CATON and CANUM checked against spread sheet: 
Imputations checked against spread sheet: 
```{r, eval = F}
file <- "HER-IIIa-2005_ok.xls" 
# Fleet E and not fleet D is used - 
#  in the summary and report it looks like E become D, so this will be corrected in the end

sheet_names <- excel_sheets(path = paste0(path_in, file))

SD20SE <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD20-SE") 
sum(unique(SD20SE$catch_t))
SD20SE$imputation <- NA
SD20SE$imputation[SD20SE$quarter == 3 & SD20SE$fleet == "E"] <- "DK, E, Q3, 20"

SD20DK <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD20-DK")
sum(unique(SD20DK$catch_t))
SD20DK$imputation <- NA
SD20DK$imputation[SD20DK$quarter == 1 & SD20DK$fleet == "C"] <- "SE, C, Q1, 20"
SD20DK$imputation[SD20DK$quarter == 2 & SD20DK$fleet == "C"] <- "SE, C, Q2, 20"
SD20DK$imputation[SD20DK$quarter == 1 & SD20DK$fleet == "E"] <- "SE, E, Q1, 20"

SD20DE <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD20-OTH")
sum(unique(SD20DE$catch_t))
SD20DE$imputation <- NA
SD20DE$imputation[SD20DE$quarter == 3 & SD20DE$fleet == "C"] <- "DK, C, Q3, 20"
SD20DE$imputation[SD20DE$quarter == 4 & SD20DE$fleet == "C"] <- "DK, C, Q4, 20"

SD20FO <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD20-OTH (2)")
sum(unique(SD20FO$catch_t))
SD20FO$imputation <- NA
SD20FO$imputation[SD20FO$quarter == 3 & SD20FO$fleet == "E"] <- "DK, E, Q3, 20"
SD20FO$imputation[SD20FO$quarter == 4 & SD20FO$fleet == "E"] <- "DK, E, Q4, 20"

SD21SE <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD21-SE")
sum(unique(SD21SE$catch_t))
SD21SE$imputation <- NA
SD21SE$imputation <- NA
SD21SE$imputation[SD21SE$quarter == 1 & SD21SE$fleet == "E"] <- "DK, C, Q1, 21"
SD21SE$imputation[SD21SE$quarter == 3 & SD21SE$fleet == "E"] <- "DK, C, Q2, 21"
SD21SE$imputation[SD21SE$quarter == 4 & SD21SE$fleet == "E"] <- "DK, C, Q3, 21"

SD21DK <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD21-DK")
sum(unique(SD21DK$catch_t))
SD21DK$imputation <- NA
SD21DK$imputation[SD21DK$quarter == 2 & SD21DK$fleet == "C"] <- "SE, C, Q2, 21"
SD21DK$imputation[SD21DK$quarter == 3 & SD21DK$fleet == "C"] <- "SE, C, Q3, 21"


c05 <- bind_rows(SD20DE, SD20DK, SD20FO, SD20SE, SD21DK, SD21SE)

# Rename fleet E to D
c05 <- subset(c05, fleet != "D")
c05$fleet[c05$fleet == "E"] <- "D"

rm(SD20DE, SD20DK, SD20FO, SD20SE, SD21DK, SD21SE)

summarise(group_by(subset(c05, wr == "8+"), year, division), ton = sum(catch_t, na.rm = T))
summarise(group_by(c05, year, division), canum = sum(canum, na.rm = T))

```

# 2004
Total CATON and CANUM checked against Thomas figures: 
Total CATON and CANUM checked against report:
Total CATON and CANUM checked against spread sheet: 
Imputations checked against spread sheet: 
```{r, eval = F}
file <- "HER-IIIa-2005_ok.xls" 
# Fleet E and not fleet D is used - 
#  in the summary and report it looks like E become D, so this will be corrected in the end

sheet_names <- excel_sheets(path = paste0(path_in, file))

SD20SE <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD20-SE") 
sum(unique(SD20SE$catch_t))
SD20SE$imputation <- NA
SD20SE$imputation[SD20SE$quarter == 3 & SD20SE$fleet == "E"] <- "DK, E, Q3, 20"

SD20DK <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD20-DK")
sum(unique(SD20DK$catch_t))
SD20DK$imputation <- NA
SD20DK$imputation[SD20DK$quarter == 1 & SD20DK$fleet == "C"] <- "SE, C, Q1, 20"
SD20DK$imputation[SD20DK$quarter == 2 & SD20DK$fleet == "C"] <- "SE, C, Q2, 20"
SD20DK$imputation[SD20DK$quarter == 1 & SD20DK$fleet == "E"] <- "SE, E, Q1, 20"

SD20DE <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD20-OTH")
sum(unique(SD20DE$catch_t))
SD20DE$imputation <- NA
SD20DE$imputation[SD20DE$quarter == 3 & SD20DE$fleet == "C"] <- "DK, C, Q3, 20"
SD20DE$imputation[SD20DE$quarter == 4 & SD20DE$fleet == "C"] <- "DK, C, Q4, 20"

SD20FO <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD20-OTH (2)")
sum(unique(SD20FO$catch_t))
SD20FO$imputation <- NA
SD20FO$imputation[SD20FO$quarter == 3 & SD20FO$fleet == "E"] <- "DK, E, Q3, 20"
SD20FO$imputation[SD20FO$quarter == 4 & SD20FO$fleet == "E"] <- "DK, E, Q4, 20"

SD21SE <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD21-SE")
sum(unique(SD21SE$catch_t))
SD21SE$imputation <- NA
SD21SE$imputation <- NA
SD21SE$imputation[SD21SE$quarter == 1 & SD21SE$fleet == "E"] <- "DK, C, Q1, 21"
SD21SE$imputation[SD21SE$quarter == 3 & SD21SE$fleet == "E"] <- "DK, C, Q2, 21"
SD21SE$imputation[SD21SE$quarter == 4 & SD21SE$fleet == "E"] <- "DK, C, Q3, 21"

SD21DK <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD21-DK")
sum(unique(SD21DK$catch_t))
SD21DK$imputation <- NA
SD21DK$imputation[SD21DK$quarter == 2 & SD21DK$fleet == "C"] <- "SE, C, Q2, 21"
SD21DK$imputation[SD21DK$quarter == 3 & SD21DK$fleet == "C"] <- "SE, C, Q3, 21"


c05 <- bind_rows(SD20DE, SD20DK, SD20FO, SD20SE, SD21DK, SD21SE)

# Rename fleet E to D
c05 <- subset(c05, fleet != "D")
c05$fleet[c05$fleet == "E"] <- "D"

rm(SD20DE, SD20DK, SD20FO, SD20SE, SD21DK, SD21SE)

summarise(group_by(subset(c05, wr == "8+"), year, division), ton = sum(catch_t, na.rm = T))
summarise(group_by(c05, year, division), canum = sum(canum, na.rm = T))

```

# 2005
Total CATON and CANUM checked against Thomas figures: ok
Total CATON and CANUM checked against report: ok
Total CATON and CANUM checked against spread sheet: ok
Imputations checked against spread sheet: ok
```{r}
file <- "HER-IIIa-2005_ok.xls" 
# Fleet E and not fleet D is used - 
#  in the summary and report it looks like E become D, so this will be corrected in the end

sheet_names <- excel_sheets(path = paste0(path_in, file))

SD20SE <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD20-SE")
sum(unique(SD20SE$catch_t))
SD20SE$imputation <- NA
SD20SE$imputation[SD20SE$quarter == 3 & SD20SE$fleet == "E"] <- "DK, E, Q3, 20"

SD20DK <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD20-DK")
sum(unique(SD20DK$catch_t))
SD20DK$imputation <- NA
SD20DK$imputation[SD20DK$quarter == 1 & SD20DK$fleet == "C"] <- "SE, C, Q1, 20"
SD20DK$imputation[SD20DK$quarter == 2 & SD20DK$fleet == "C"] <- "SE, C, Q2, 20"
SD20DK$imputation[SD20DK$quarter == 1 & SD20DK$fleet == "E"] <- "SE, E, Q1, 20"

SD20DE <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD20-OTH")
sum(unique(SD20DE$catch_t))
SD20DE$imputation <- NA
SD20DE$imputation[SD20DE$quarter == 3 & SD20DE$fleet == "C"] <- "DK, C, Q3, 20"
SD20DE$imputation[SD20DE$quarter == 4 & SD20DE$fleet == "C"] <- "DK, C, Q4, 20"

SD20FO <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD20-OTH (2)")
sum(unique(SD20FO$catch_t))
SD20FO$imputation <- NA
SD20FO$imputation[SD20FO$quarter == 3 & SD20FO$fleet == "E"] <- "DK, E, Q3, 20"
SD20FO$imputation[SD20FO$quarter == 4 & SD20FO$fleet == "E"] <- "DK, E, Q4, 20"

SD21SE <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD21-SE")
sum(unique(SD21SE$catch_t))
SD21SE$imputation <- NA
SD21SE$imputation <- NA
SD21SE$imputation[SD21SE$quarter == 1 & SD21SE$fleet == "E"] <- "DK, E, Q1, 21"
SD21SE$imputation[SD21SE$quarter == 3 & SD21SE$fleet == "E"] <- "DK, E, Q2, 21"
SD21SE$imputation[SD21SE$quarter == 4 & SD21SE$fleet == "E"] <- "DK, E, Q3, 21"

SD21DK <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD21-DK")
sum(unique(SD21DK$catch_t))
SD21DK$imputation <- NA
SD21DK$imputation[SD21DK$quarter == 2 & SD21DK$fleet == "C"] <- "SE, C, Q2, 21"
SD21DK$imputation[SD21DK$quarter == 3 & SD21DK$fleet == "C"] <- "SE, C, Q3, 21"


c05 <- bind_rows(SD20DE, SD20DK, SD20FO, SD20SE, SD21DK, SD21SE)

# Rename fleet E to D
c05 <- subset(c05, fleet != "D")
c05$fleet[c05$fleet == "E"] <- "D"

rm(SD20DE, SD20DK, SD20FO, SD20SE, SD21DK, SD21SE)

summarise(group_by(subset(c05, wr == "8+"), year, division), ton = sum(catch_t, na.rm = T))
summarise(group_by(c05, year, division), canum = sum(canum, na.rm = T))

```

# 2006
Total CATON and CANUM checked against Thomas figures: CANUM ok, but CATON too high in and it looks like Kattegat and Skagerrak are swapped
Total CATON and CANUM checked against report: ok
Total CATON and CANUM checked against spread sheet: ok
Imputations checked against spread sheet: ok
```{r}
file <- "HER-IIIa-2006.xls" 

sheet_names <- excel_sheets(path = paste0(path_in, file))

SD20SE <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD20-SE") 
sum(unique(SD20SE$catch_t))
SD20SE$imputation <- NA
SD20SE$imputation[SD20SE$quarter == 1 & SD20SE$fleet == "D"] <- "SE, C, Q1, 20"
SD20SE$imputation[SD20SE$quarter == 2 & SD20SE$fleet == "D"] <- "SE, C, Q2, 20"
SD20SE$imputation[SD20SE$quarter == 3 & SD20SE$fleet == "D"] <- "SE, C, Q3, 20"
SD20SE$imputation[SD20SE$quarter == 4 & SD20SE$fleet == "D"] <- "SE, C, Q4, 20"

SD20DK <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD20-DK")
sum(unique(SD20DK$catch_t))
SD20DK$imputation <- NA
SD20DK$imputation[SD20DK$quarter == 4 & SD20DK$fleet == "C"] <- "SE, C, Q4, 20"
SD20DK$imputation[SD20DK$quarter == 4 & SD20DK$fleet == "D"] <- "SE, C, Q4, 20"

SD20DE <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD20-OTH")
sum(unique(SD20DE$catch_t))
SD20DE$imputation <- NA
SD20DE$imputation[SD20DE$quarter == 3 & SD20DE$fleet == "C"] <- "DK, C, Q3, 20"

SD21SE <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD21-SE")
sum(unique(SD21SE$catch_t))
SD21SE$imputation <- NA
SD21SE$imputation[SD21SE$quarter == 1 & SD21SE$fleet == "D"] <- "SE, C, Q1, 21"
SD21SE$imputation[SD21SE$quarter == 3 & SD21SE$fleet == "D"] <- "SE, C, Q3, 21"
SD21SE$imputation[SD21SE$quarter == 4 & SD21SE$fleet == "D"] <- "SE, C, Q4, 21"

SD21DK <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD21-DK")
sum(unique(SD21DK$catch_t))
SD21DK$imputation <- NA
SD21DK$imputation[SD21DK$quarter == 2 & SD21DK$fleet == "D"] <- "DK, D, Q1, 21"


c06 <- bind_rows(SD20DE, SD20DK, SD20SE, SD21DK, SD21SE)

rm(SD20DE, SD20DK, SD20SE, SD21DK, SD21SE)

summarise(group_by(subset(c06, wr == "8+"), year, division), ton = sum(catch_t, na.rm = T))
summarise(group_by(c06, year, division), canum = sum(canum, na.rm = T))

```

# 2007
Total CATON and CANUM checked against Thomas figures: 
Total CATON and CANUM checked against report:
Total CATON and CANUM checked against spread sheet: 
Imputations checked against spread sheet: 
```{r}
file <- "HER-IIIa-2007new.xls"

sheet_names <- excel_sheets(path = paste0(path_in, file))

SD20NO <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD20-NO")
sum(unique(SD20NO$catch_t))
SD20NO$imputation <- NA
SD20NO$imputation[SD20NO$quarter == 1 & SD20NO$fleet == "C"] <- "DK, C, Q2, 20"
SD20NO$imputation[SD20NO$quarter == 2 & SD20NO$fleet == "C"] <- "DK, C, Q2, 20"
SD20NO$imputation[SD20NO$quarter == 3 & SD20NO$fleet == "C"] <- "DK, C, Q3, 20"
SD20NO$imputation[SD20NO$quarter == 4 & SD20NO$fleet == "C"] <- "DK, C, Q3, 20"

SD20SE <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD20-SE") # No imputations
sum(unique(SD20SE$catch_t))
SD20SE$imputation <- NA
SD20SE$imputation[SD20SE$quarter == 1 & SD20SE$fleet == "D"] <- "SE, C, Q1, 20"
SD20SE$imputation[SD20SE$quarter == 2 & SD20SE$fleet == "D"] <- "SE, C, Q2, 20"
SD20SE$imputation[SD20SE$quarter == 3 & SD20SE$fleet == "D"] <- "SE, C, Q3, 20"
SD20SE$imputation[SD20SE$quarter == 4 & SD20SE$fleet == "D"] <- "SE, C, Q4, 20"

SD20DK <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD20-DK")
sum(unique(SD20DK$catch_t))
SD20DK$imputation <- NA
SD20DK$imputation[SD20DK$quarter == 2 & SD20DK$fleet == "D"] <- "DK, D, Q1, 21"
SD20DK$imputation[SD20DK$quarter == 4 & SD20DK$fleet == "D"] <- "DK, D, Q4, 21"
SD20DK$imputation[SD20DK$quarter == 4 & SD20DK$fleet == "C"] <- "DK, C, Q3, 20"

SD20DE <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD20-OTH")
sum(unique(SD20DE$catch_t))
SD20DE$imputation <- NA
SD20DE$imputation[SD20DE$quarter == 3 & SD20DE$fleet == "C"] <- "DK, C, Q3, 20"

SD21SE <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD21-SE")
sum(unique(SD21SE$catch_t))
SD21SE$imputation <- NA
SD21SE$imputation <- NA
SD21SE$imputation[SD21SE$quarter == 1 & SD21SE$fleet == "D"] <- "SE, C, Q1, 21"
SD21SE$imputation[SD21SE$quarter == 2 & SD21SE$fleet == "D"] <- "SE, C, Q2, 21"
SD21SE$imputation[SD21SE$quarter == 3 & SD21SE$fleet == "D"] <- "SE, C, Q3, 21"
SD21SE$imputation[SD21SE$quarter == 4 & SD21SE$fleet == "D"] <- "SE, C, Q4, 21"

SD21DK <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD21-DK")
sum(unique(SD21DK$catch_t))
SD21DK$imputation <- NA
SD21DK$imputation[SD21DK$quarter == 2 & SD21DK$fleet == "C"] <- "DK, C, Q2, 20"
SD21DK$imputation[SD21DK$quarter == 2 & SD21DK$fleet == "D"] <- "DK, D, Q1, 21"


c07 <- bind_rows(SD20DE, SD20DK, SD20NO, SD20SE, SD21DK, SD21SE)

rm(SD20DE, SD20DK, SD20NO, SD20SE, SD21DK, SD21SE)

summarise(group_by(subset(c07, wr == "8+"), year, division), ton = sum(catch_t, na.rm = T))
summarise(group_by(c07, year, division), canum = sum(canum, na.rm = T))

```


# 2008
Total CATON and CANUM checked against Thomas figures: 
Total CATON and CANUM checked against report:
Total CATON and CANUM checked against spread sheet: 
Imputations checked against spread sheet: 
```{r}
file <- "HER-IIIa-2008new.xls"

sheet_names <- excel_sheets(path = paste0(path_in, file))

SD20NO <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD20-NO")
sum(unique(SD20NO$catch_t))
SD20NO$imputation <- NA
SD20NO$imputation[SD20NO$quarter == 1 & SD20NO$fleet == "C"] <- "DK, C, Q1, 20"
SD20NO$imputation[SD20NO$quarter == 2 & SD20NO$fleet == "C"] <- "DK, C, Q1, 20"
SD20NO$imputation[SD20NO$quarter == 3 & SD20NO$fleet == "C"] <- "DK, C, Q3, 20"
SD20NO$imputation[SD20NO$quarter == 4 & SD20NO$fleet == "C"] <- "DK, C, Q3, 20"

SD20SE <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD20-SE")
sum(unique(SD20SE$catch_t))
SD20SE$imputation[SD20SE$quarter == 1 & SD20SE$fleet == "D"] <- "SE, C, Q1, 20"
SD20SE$imputation[SD20SE$quarter == 2 & SD20SE$fleet == "D"] <- "SE, C, Q2, 20"
SD20SE$imputation[SD20SE$quarter == 3 & SD20SE$fleet == "D"] <- "SE, C, Q3, 20"
SD20SE$imputation[SD20SE$quarter == 4 & SD20SE$fleet == "D"] <- "SE, C, Q4, 20"

SD20DK <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD20-DK")
sum(unique(SD20DK$catch_t))
SD20DK$imputation <- NA
SD20DK$imputation[SD20DK$quarter == 2 & SD20DK$fleet == "C"] <- "DK, C, Q1, 20"
SD20DK$imputation[SD20DK$quarter == 4 & SD20DK$fleet == "C"] <- "DK, C, Q3, 20"
SD20DK$imputation[SD20DK$quarter == 3 & SD20DK$fleet == "D"] <- "DK, D, Q4, 20"

SD20DE <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD20-OTH")
sum(unique(SD20DE$catch_t))
SD20DE$imputation <- NA
SD20DE$imputation[SD20DE$quarter == 2 & SD20DE$fleet == "C"] <- "DK, C, Q1, 20"
SD20DE$imputation[SD20DE$quarter == 4 & SD20DE$fleet == "C"] <- "DK, C, Q3, 20"

SD21SE <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD21-SE")
sum(unique(SD21SE$catch_t))
SD21SE$imputation <- NA
SD21SE$imputation[SD21SE$quarter == 1 & SD21SE$fleet == "D"] <- "SE, C, Q1, 21"
SD21SE$imputation[SD21SE$quarter == 2 & SD21SE$fleet == "D"] <- "SE, C, Q2, 21"
SD21SE$imputation[SD21SE$quarter == 3 & SD21SE$fleet == "D"] <- "SE, C, Q3, 21"
SD21SE$imputation[SD21SE$quarter == 4 & SD21SE$fleet == "D"] <- "SE, C, Q4, 21"

SD21DK <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD21-DK")
sum(unique(SD21DK$catch_t))
SD21DK$imputation <- NA
SD21DK$imputation[SD21DK$quarter == 2 & SD21DK$fleet == "C"] <- "DK, C, Q1, 21"
SD21DK$imputation[SD21DK$quarter == 4 & SD21DK$fleet == "C"] <- "DK, C, Q3, 21"
SD21DK$imputation[SD21DK$quarter == 4 & SD21DK$fleet == "D"] <- "DK, D, Q3, 21"


c08 <- bind_rows(SD20DE, SD20DK, SD20NO, SD20SE, SD21DK, SD21SE)

rm(SD20DE, SD20DK, SD20NO, SD20SE, SD21DK, SD21SE)

summarise(group_by(subset(c08, wr == "8+"), year, division), ton = sum(catch_t, na.rm = T))
summarise(group_by(c08, year, division), canum = sum(canum, na.rm = T))

# Preliminary check against Thomas figures and current time series ok
```


# 2009
Total CATON and CANUM checked against Thomas figures: 
Total CATON and CANUM checked against report:
Total CATON and CANUM checked against spread sheet: 
Imputations checked against spread sheet: 
```{r}
file <- "HER-IIIa-2009.xls"

sheet_names <- excel_sheets(path = paste0(path_in, file))

SD20NO <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD20-NO")
sum(unique(SD20NO$catch_t))
SD20NO$imputation <- NA
SD20NO$imputation[SD20NO$quarter == 1 & SD20NO$fleet == "C"] <- "DK, C, Q2, 20"
SD20NO$imputation[SD20NO$quarter == 2 & SD20NO$fleet == "C"] <- "DK, C, Q2, 20"
SD20NO$imputation[SD20NO$quarter == 3 & SD20NO$fleet == "C"] <- "DK, C, Q3, 20"
SD20NO$imputation[SD20NO$quarter == 4 & SD20NO$fleet == "C"] <- "DK, C, Q4, 20"

SD20SE <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD20-SE") # No imputations
sum(unique(SD20SE$catch_t))
SD20SE$imputation[SD20SE$quarter == 1 & SD20SE$fleet == "D"] <- "SE, C, Q1, 20"
SD20SE$imputation[SD20SE$quarter == 2 & SD20SE$fleet == "D"] <- "SE, C, Q2, 20"
SD20SE$imputation[SD20SE$quarter == 3 & SD20SE$fleet == "D"] <- "SE, C, Q3, 20"
SD20SE$imputation[SD20SE$quarter == 4 & SD20SE$fleet == "D"] <- "SE, C, Q4, 20"

SD20DK <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD20-DK")
sum(unique(SD20DK$catch_t))
SD20DK$imputation <- NA
SD20DK$imputation[SD20DK$quarter == 1 & SD20DK$fleet == "C"] <- "DK, C, Q2, 20"
SD20DK$imputation[SD20DK$quarter == 1 & SD20DK$fleet == "D"] <- "DK, D, Q2, 20"

SD20DE <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD20-OTH")
sum(unique(SD20DE$catch_t))
SD20DE$imputation <- NA
SD20DE$imputation[SD20DE$quarter == 3 & SD20DE$fleet == "C"] <- "DK, C, Q3, 20"
SD20DE$imputation[SD20DE$quarter == 4 & SD20DE$fleet == "C"] <- "DK, C, Q4, 20"

SD21SE <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD21-SE")
sum(unique(SD21SE$catch_t))
SD21SE$imputation <- NA
SD21SE$imputation[SD21SE$quarter == 1 & SD21SE$fleet == "D"] <- "SE, C, Q1, 21"
SD21SE$imputation[SD21SE$quarter == 3 & SD21SE$fleet == "D"] <- "SE, C, Q3, 21"
SD21SE$imputation[SD21SE$quarter == 4 & SD21SE$fleet == "D"] <- "SE, C, Q4, 21"
SD20SE$imputation[SD20SE$quarter == 2 & SD20SE$fleet == "C"] <- "SE, C, Q1, 21"

SD21DK <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD21-DK")
sum(unique(SD21DK$catch_t))
SD21DK$imputation <- NA
SD21DK$imputation[SD21DK$quarter == 2 & SD21DK$fleet == "C"] <- "DK, C, Q1, 21"
SD21DK$imputation[SD21DK$quarter == 3 & SD21DK$fleet == "C"] <- "DK, C, Q4, 21"

SD21DE <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD21-OTH")
sum(unique(SD21DE$catch_t))
SD21DE$imputation <- NA
SD21DE$imputation[SD21DE$quarter == 1 & SD21DE$fleet == "C"] <- "DK, C, Q1, 21"
SD21DE$imputation[SD21DE$quarter == 3 & SD21DE$fleet == "C"] <- "DK, C, Q4, 21"


c09 <- bind_rows(SD20DE, SD20DK, SD20NO, SD20SE, SD21DK, SD21SE, SD21DE)

rm(SD20DE, SD20DK, SD20NO, SD20SE, SD21DK, SD21SE, SD21DE)

summarise(group_by(subset(c09, wr == "8+"), year, division), ton = sum(catch_t, na.rm = T))
summarise(group_by(c09, year, division), canum = sum(canum, na.rm = T))

# Preliminary check against Thomas figures and current time series ok
```


# 2010
Total CATON and CANUM checked against Thomas figures: 
Total CATON and CANUM checked against report:
Total CATON and CANUM checked against spread sheet: 
Imputations checked against spread sheet: 
```{r}
file <- "HER-IIIa-2010.xls"

sheet_names <- excel_sheets(path = paste0(path_in, file))

SD20NO <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD20-NO")
sum(unique(SD20NO$catch_t))
SD20NO$imputation <- NA
SD20NO$imputation[SD20NO$quarter == 1 & SD20NO$fleet == "C"] <- "DK, C, Q1, 20" 
SD20NO$imputation[SD20NO$quarter == 2 & SD20NO$fleet == "C"] <- "DK, C, Q1, 20"
SD20NO$imputation[SD20NO$quarter == 4 & SD20NO$fleet == "C"] <- "NO, C, Q1, 20"

SD20SE <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD20-SE") # No imputations
sum(unique(SD20SE$catch_t))

SD20DK <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD20-DK")
sum(unique(SD20DK$catch_t))
SD20DK$imputation <- NA
SD20DK$imputation[SD20DK$quarter == 1 & SD20DK$fleet == "C"] <- "DK, C, Q2, 20"
SD20DK$imputation[SD20DK$quarter == 1 & SD20DK$fleet == "D"] <- "DK, D, Q2, 20"

SD20DE <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD20-OTH")
sum(unique(SD20DE$catch_t))
SD20DE$imputation <- NA

SD20FO <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD20-OTH (2)")
sum(unique(SD20FO$catch_t))
SD20FO$imputation <- NA
SD20FO$imputation[SD20FO$quarter == 4 & SD20FO$fleet == "C"] <- "DK, D, Q4, 20"

SD20LI <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD20-OTH (3)")
sum(unique(SD20LI$catch_t))
SD20LI$imputation <- NA
SD20LI$imputation[SD20LI$quarter == 3 & SD20LI$fleet == "C"] <- "DK, D, Q3, 20"

SD21SE <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD21-SE")
sum(unique(SD21SE$catch_t))
SD21SE$imputation <- NA

SD21DK <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD21-DK")
sum(unique(SD21DK$catch_t))
SD21DK$imputation <- NA
SD21DK$imputation[SD21DK$quarter == 2 & SD21DK$fleet == "C"] <- "DK, C, Q1, 21"

c10 <- bind_rows(SD20DE, SD20DK, SD20NO, SD20SE, SD20FO, SD20LI, SD21DK, SD21SE)

rm(SD20DE, SD20DK, SD20NO, SD20SE, SD20FO, SD20LI, SD21DK, SD21SE)

summarise(group_by(subset(c10, wr == "8+"), year, division), ton = sum(catch_t, na.rm = T))
summarise(group_by(c10, year, division), canum = sum(canum, na.rm = T))

# Preliminary check against Thomas figures and current time series ok
```

# 2011
Total CATON and CANUM checked against Thomas figures: 
Total CATON and CANUM checked against report:
Total CATON and CANUM checked against spread sheet: 
Imputations checked against spread sheet: 
```{r}
file <- "HER-IIIa-2011.xls"

sheet_names <- excel_sheets(path = paste0(path_in, file))

SD20NO <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD20-NO")
sum(unique(SD20NO$catch_t))
SD20NO$imputation <- NA
SD20NO$imputation[SD20NO$quarter == 1 & SD20NO$fleet == "C"] <- "HC_Q1_3aN_DEN"
SD20NO$imputation[SD20NO$quarter == 2 & SD20NO$fleet == "C"] <- "HC_Q1_3aN_DEN"
SD20NO$imputation[SD20NO$quarter == 3 & SD20NO$fleet == "C"] <- "HC_Q3_3aN_DEN"
SD20NO$imputation[SD20NO$quarter == 4 & SD20NO$fleet == "C"] <- "HC_Q3_3aN_DEN"

SD20SE <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD20-SE") # No imputations
sum(unique(SD20SE$catch_t))

SD20DK <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD20-DK")
sum(unique(SD20DK$catch_t))
SD20DK$imputation <- NA
SD20DK$imputation[SD20DK$quarter == 1 & SD20DK$fleet == "C"] <- "HC_Q1_3aN_DEN"
SD20DK$imputation[SD20DK$quarter == 4 & SD20DK$fleet == "C"] <- "HC_Q3_3aN_DEN"

SD20DE <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD20-OTH")
sum(unique(SD20DE$catch_t))
SD20DE$imputation <- NA
SD20DE$imputation[SD20DE$quarter == 4 & SD20DE$fleet == "C"] <- "DEN_IIIaN_Q4"

SD21SE <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD21-SE")
sum(unique(SD21SE$catch_t))
SD21SE$imputation <- NA

SD21DK <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD21-DK")
sum(unique(SD21DK$catch_t))
SD21DK$imputation <- NA

c11 <- bind_rows(SD20DE, SD20DK, SD20NO, SD20SE, SD21DK, SD21SE)

rm(SD20DE, SD20DK, SD20NO, SD20SE, SD21DK, SD21SE)

summarise(group_by(subset(c11, wr == "8+"), year, division), ton = sum(catch_t, na.rm = T))
summarise(group_by(c11, year, division), canum = sum(canum, na.rm = T))

# Preliminary check against Thomas figures and current time series ok
```

# 2012
Total CATON and CANUM checked against Thomas figures: 
Total CATON and CANUM checked against report:
Total CATON and CANUM checked against spread sheet: 
Imputations checked against spread sheet: 
```{r}
file <- "HER-IIIa-2012.xls"

sheet_names <- excel_sheets(path = paste0(path_in, file))

SD20NO <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD20-NO") # No imputations
sum(unique(SD20NO$catch_t))

SD20SE <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD20-SE") # No imputations
sum(unique(SD20SE$catch_t))

SD20DK <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD20-DK")
sum(unique(SD20DK$catch_t))
SD20DK$imputation <- NA
SD20DK$imputation[SD20DK$quarter == 1 & SD20DK$fleet == "C"] <- "SWE_IIIaN_Q1"
SD20DK$imputation[SD20DK$quarter == 2 & SD20DK$fleet == "C"] <- "SWE_IIIaN_Q2"

SD20DE <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD20-OTH")
sum(unique(SD20DE$catch_t))
SD20DE$imputation <- NA
SD20DE$imputation[SD20DE$quarter == 3 & SD20DE$fleet == "C"] <- "DEN_IIIaN_Q3"
SD20DE$imputation[SD20DE$quarter == 4 & SD20DE$fleet == "C"] <- "DEN_IIIaN_Q4"

SD21SE <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD21-SE")
sum(unique(SD21SE$catch_t))
SD21SE$imputation <- NA
SD21SE$imputation[SD21SE$quarter == 2 & SD21SE$fleet == "C"] <- "SWE_IIIaS_Q1"
SD21SE$imputation[SD21SE$quarter == 3 & SD21SE$fleet == "C"] <- "SWE_IIIaN_Q3"
SD21SE$imputation[SD21SE$quarter == 4 & SD21SE$fleet == "C"] <- "SWE_IIIaN_Q4"

SD21DK <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD21-DK")
sum(unique(SD21DK$catch_t))
SD21DK$imputation <- NA
SD21DK$imputation[SD21DK$quarter == 1 & SD21DK$fleet == "C"] <- "SWE_IIIaS_Q1"
SD21DK$imputation[SD21DK$quarter == 2 & SD21DK$fleet == "C"] <- "SWE_IIIaS_Q1"

c12 <- bind_rows(SD20DE, SD20DK, SD20NO, SD20SE, SD21DK, SD21SE)

rm(SD20DE, SD20DK, SD20NO, SD20SE, SD21DK, SD21SE)

summarise(group_by(subset(c12, wr == "8+"), year, division), ton = sum(catch_t, na.rm = T))
summarise(group_by(c12, year), canum = sum(canum, na.rm = T))

# Preliminary check against Thomas figures and current time series ok
```

# 2013
Total CATON and CANUM checked against Thomas figures: 
Total CATON and CANUM checked against report:
Total CATON and CANUM checked against spread sheet: 
Imputations checked against spread sheet: 
```{r}
file <- "HER-IIIa-2013.xls"

sheet_names <- excel_sheets(path = paste0(path_in, file))

SD20NO <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD20-NO")
sum(unique(SD20NO$catch_t))
SD20NO$imputation[SD20NO$quarter == 1 & SD20NO$fleet == "C"] <- "SWE_IIIaN_Q1"
SD20NO$imputation[SD20NO$quarter == 2 & SD20NO$fleet == "C"] <- "SWE_IIIaN_Q2"
SD20NO$imputation[SD20NO$quarter == 3 & SD20NO$fleet == "C"] <- "NO_IIIaN_Q4"

SD20SE <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD20-SE") # No imputations
sum(unique(SD20SE$catch_t))

SD20DK <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD20-DK")
sum(unique(SD20DK$catch_t))
SD20DK$imputation <- NA
SD20DK$imputation[SD20DK$quarter == 1 & SD20DK$fleet == "C"] <- "SWE_IIIaN_Q1"
SD20DK$imputation[SD20DK$quarter == 2 & SD20DK$fleet == "C"] <- "SWE_IIIaN_Q2"

SD20DE <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD20-OTH")
sum(unique(SD20DE$catch_t))
SD20DE$imputation <- NA
SD20DE$imputation[SD20DE$quarter == 3 & SD20DE$fleet == "C"] <- "DEN_IIIaN_Q3"
SD20DE$imputation[SD20DE$quarter == 4 & SD20DE$fleet == "C"] <- "DEN_IIIaN_Q4"

SD21SE <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD21-SE")
sum(unique(SD21SE$catch_t))
SD21SE$imputation <- NA
SD21SE$imputation[SD21SE$quarter == 2 & SD21SE$fleet == "C"] <- "SWE_IIIaS_Q1"
SD21SE$imputation[SD21SE$quarter == 3 & SD21SE$fleet == "C"] <- "SWE_IIIaS_Q4"

SD21DK <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD21-DK")
sum(unique(SD21DK$catch_t))
SD21DK$imputation <- NA
SD21DK$imputation[SD21DK$quarter == 1 & SD21DK$fleet == "C"] <- "SWE_IIIaS_Q1"
SD21DK$imputation[SD21DK$quarter == 2 & SD21DK$fleet == "C"] <- "SWE_IIIaS_Q1"

c13 <- bind_rows(SD20DE, SD20DK, SD20NO, SD20SE, SD21DK, SD21SE)

rm(SD20DE, SD20DK, SD20NO, SD20SE, SD21DK, SD21SE)

summarise(group_by(subset(c13, wr == "8+"), year, division), ton = sum(catch_t, na.rm = T))
summarise(group_by(c13, year, division), canum = sum(canum, na.rm = T))

# Preliminary check against Thomas figures and current time series ok
```

# 2014
Total CATON and CANUM checked against Thomas figures: 
Total CATON and CANUM checked against report:
Total CATON and CANUM checked against spread sheet: 
Imputations checked against spread sheet: 
```{r}
file <- "HER-IIIa-2014.xls"

sheet_names <- excel_sheets(path = paste0(path_in, file))

SD20NO <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD20-NO")
sum(unique(SD20NO$catch_t))
SD20NO$imputation[SD20NO$quarter == 1 & SD20NO$fleet == "C"] <- "NO_IIIaN_Q2"
SD20NO$imputation[SD20NO$quarter == 3 & SD20NO$fleet == "C"] <- "DEN_Q3_20"
SD20NO$imputation[SD20NO$quarter == 4 & SD20NO$fleet == "C"] <- "DEN_Q4_20"

SD20SE <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD20-SE") # No imputations
sum(unique(SD20SE$catch_t))

SD20DK <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD20-DK")
sum(unique(SD20DK$catch_t))
SD20DK$imputation <- NA
SD20DK$imputation[SD20DK$quarter == 2 & SD20DK$fleet == "C"] <- "DEN_Q1_20"
SD20DK$imputation[SD20DK$quarter == 2 & SD20DK$fleet == "D"] <- "DEN_Q2_21"
SD20DK$imputation[SD20DK$quarter == 4 & SD20DK$fleet == "D"] <- "DEN_Q3_20"

SD20DE <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD20-OTH")
sum(unique(SD20DE$catch_t))
SD20DE$imputation <- NA
SD20DE$imputation[SD20DE$quarter == 4 & SD20DE$fleet == "C"] <- "DEN_IIIaN_Q4"

SD20FO <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD20-OTH (2)")
sum(unique(SD20FO$catch_t))
SD20FO$imputation <- NA
SD20FO$imputation[SD20FO$quarter == 3 & SD20FO$fleet == "C"] <- "DEN_Q3_Fleet C"

SD21SE <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD21-SE")
sum(unique(SD21SE$catch_t))
SD21SE$imputation <- NA # No imputations

SD21DK <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD21-DK")
sum(unique(SD21DK$catch_t))
SD21DK$imputation <- NA
SD21DK$imputation[SD21DK$quarter == 2 & SD21DK$fleet == "C"] <- "DNK_IIIaS_Q1"
SD21DK$imputation[SD21DK$quarter == 3 & SD21DK$fleet == "C"] <- "DNK_IIIaN_Q3"
SD21DK$imputation[SD21DK$quarter == 4 & SD21DK$fleet == "C"] <- "DNK_IIIaN_Q4"

c14 <- bind_rows(SD20DE, SD20DK, SD20NO, SD20SE, SD20FO, SD21DK, SD21SE)

rm(SD20DE, SD20DK, SD20NO, SD20SE, SD20FO, SD21DK, SD21SE)

summarise(group_by(subset(c14, wr == "8+"), year, division), ton = sum(catch_t, na.rm = T))
summarise(group_by(c14, year, division), canum = sum(canum, na.rm = T))

# Preliminary check against Thomas figures and current time series ok
```

# 2015
Total CATON and CANUM checked against Thomas figures: 
Total CATON and CANUM checked against report:
Total CATON and CANUM checked against spread sheet: 
Imputations checked against spread sheet: 
```{r}
file <- "HER-IIIa-2015.xls"

sheet_names <- excel_sheets(path = paste0(path_in, file))

SD20NO <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD20-NO")
sum(unique(SD20NO$catch_t))
SD20NO$imputation <- NA
SD20NO$imputation[SD20NO$quarter == 1 & SD20NO$fleet == "C"] <- "SWE_20_Q1"
SD20NO$imputation[SD20NO$quarter == 1 & SD20NO$fleet == "C"] <- "SWE_20_Q1"
SD20NO$imputation[SD20NO$quarter == 3 & SD20NO$fleet == "C"] <- "DEN_20_C_Q3"
SD20NO$imputation[SD20NO$quarter == 4 & SD20NO$fleet == "C"] <- "SWE_20_Q4"

SD20SE <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD20-SE") # No imputations
sum(unique(SD20SE$catch_t))
SD20SE$imputation <- NA
SD20SE$imputation[SD20SE$quarter == 2 & SD20SE$fleet == "C"] <- "SWE_20_Q1"

SD20DK <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD20-DK")
sum(unique(SD20DK$catch_t))
SD20DK$imputation <- NA
SD20DK$imputation[SD20DK$quarter == 2 & SD20DK$fleet == "C"] <- "SWE_C_20_Q2"
SD20DK$imputation[SD20DK$quarter == 1 & SD20DK$fleet == "D"] <- "D_21_DK_Q1"
SD20DK$imputation[SD20DK$quarter == 2 & SD20DK$fleet == "D"] <- "D_21_DK_Q2"

SD20DE <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD20-OTH")
sum(unique(SD20DE$catch_t))
SD20DE$imputation <- NA
SD20DE$imputation[SD20DE$quarter == 4 & SD20DE$fleet == "C"] <- "SWE_IIIaN_Q4"

SD20FO <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD20-OTH (2)")
sum(unique(SD20FO$catch_t))
SD20FO$imputation <- NA
SD20FO$imputation[SD20FO$quarter == 1 & SD20FO$fleet == "C"] <- "SWE_20_Q1"

SD20NL <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD20-OTH (3)")
sum(unique(SD20NL$catch_t))
SD20NL$imputation <- NA
SD20NL$imputation[SD20FO$quarter == 3 & SD20FO$fleet == "C"] <- "DEN_20_C_Q3"

SD21SE <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD21-SE")
sum(unique(SD21SE$catch_t))
SD21SE$imputation <- NA # No imputations

SD21DK <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD21-DK")
sum(unique(SD21DK$catch_t))
SD21DK$imputation <- NA
SD21DK$imputation[SD21DK$quarter == 1 & SD21DK$fleet == "C"] <- "SWE_21_Q1"
SD21DK$imputation[SD21DK$quarter == 2 & SD21DK$fleet == "C"] <- "SWE_21_Q2"

c15 <- bind_rows(SD20DE, SD20DK, SD20NO, SD20SE, SD20FO, SD20NL, SD21DK, SD21SE)

rm(SD20DE, SD20DK, SD20NO, SD20SE, SD20FO, SD20NL, SD21DK, SD21SE)

summarise(group_by(subset(c15, wr == "8+"), year, division), ton = sum(catch_t, na.rm = T))
summarise(group_by(c15, year, division), canum = sum(canum, na.rm = T))

# Preliminary check against Thomas figures and current time series ok
```

# Combine
```{r}

dat <- bind_rows(c05, c06, c07, c08, c09, c10, c11, c12, c13, c14, c15)
rm(c05, c06, c07, c08, c09, c10, c11, c12, c13, c14, c15)
unique(dat$year)
unique(dat$ctry)

# Clean up codes
dat$area <- NA
dat$area[dat$division == "Kattegat"] <- "27.3.a.21"
dat$area[dat$division == "Skagerrak"] <- "27.3.a.20"

```

# Output
```{r}

write.table(dat, "./data/canum_old_format_3a.csv", row.names = F, sep = ";")

```

