---
title: "read_in"
author: "Kirsten Birch Håkansson, DTU Aqua"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = F, message = F)

library(readxl)
library(dplyr)

source("../utils/read_canum_sheet_old_format_22-24.R")

path_in <- "../boot/data/historical_data/sc_sheets_old_format/"

```

# 2000
```{r}
file <- "INT-Herring-22-24-00_end.xls" 
# Fleet E and not fleet D is used - 
#  in the summary and report it looks like E become D, so this will be corrected in the end

sheet_names <- excel_sheets(path = paste0(path_in, file))

PL <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "22-24-Pl")
sum(unique(PL$catch_t))

DE <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "22-24- GE")
sum(unique(DE$catch_t))
DE$imputation <- NA
DE$imputation[DE$quarter == 3 & DE$division == "22"] <- "Imputed"
DE$imputation[DE$quarter == 4 & DE$division == "22"] <- "Imputed"
DE$imputation[DE$quarter == 3 & DE$division == "24"] <- "Imputed"
DE$imputation[DE$quarter == 4 & DE$division == "24"] <- "Imputed"

DK <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "22-24-DK")
sum(unique(DK$catch_t))
DK$imputation <- NA
DK$imputation[DK$quarter == 1 & DK$division == "23"] <- "Imputed"
DK$imputation[DK$quarter == 2 & DK$division == "23"] <- "Imputed"
DK$imputation[DK$quarter == 3 & DK$division == "23"] <- "Imputed"
DK$imputation[DK$quarter == 4 & DK$division == "23"] <- "Imputed"

SE <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "22-24-SE")
sum(unique(SE$catch_t))
SE$imputation[SE$quarter == 1 & SE$division == "23"] <- "Imputed"
SE$imputation[SE$quarter == 2 & SE$division == "23"] <- "Imputed"
SE$imputation[SE$quarter == 3 & SE$division == "23"] <- "Imputed"
SE$imputation[SE$quarter == 4 & SE$division == "23"] <- "Imputed"
SE$imputation[SE$quarter == 2 & SE$division == "24"] <- "Imputed"

c00 <- bind_rows(PL, DE, DK, SE)

rm(PL, DE, DK, SE)

summarise(group_by(subset(c00, wr == "8+"), year, division), ton = sum(catch_t, na.rm = T))
summarise(group_by(c00, year, division), canum = sum(canum, na.rm = T))

```

# 2001
```{r}
file <- "T_3-3-9_INT-herring_22-24_2001 revised.xls" 
# Fleet E and not fleet D is used - 
#  in the summary and report it looks like E become D, so this will be corrected in the end

sheet_names <- excel_sheets(path = paste0(path_in, file))

PL <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "22-24-Pl")
sum(unique(PL$catch_t))

DE <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "22-24- GE")
sum(unique(DE$catch_t))
DE$imputation <- NA
DE$imputation[DE$quarter == 1 & DE$division == "22"] <- "Imputed"
DE$imputation[DE$quarter == 2 & DE$division == "22"] <- "Imputed"
DE$imputation[DE$quarter == 3 & DE$division == "22"] <- "Imputed"
DE$imputation[DE$quarter == 4 & DE$division == "22"] <- "Imputed"
DE$imputation[DE$quarter == 3 & DE$division == "24"] <- "Imputed"
DE$imputation[DE$quarter == 4 & DE$division == "24"] <- "Imputed"

DK <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "22-24-DK")
sum(unique(DK$catch_t))
DK$imputation <- NA
DK$imputation[DK$quarter == 1 & DK$division == "23"] <- "Imputed"
DK$imputation[DK$quarter == 2 & DK$division == "23"] <- "Imputed"
DK$imputation[DK$quarter == 3 & DK$division == "23"] <- "Imputed"
DK$imputation[DK$quarter == 4 & DK$division == "23"] <- "Imputed"
DK$imputation[DK$quarter == 3 & DK$division == "24"] <- "Imputed"

SE <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "22-24-SE")
sum(unique(SE$catch_t))
SE$imputation[SE$quarter == 1 & SE$division == "23"] <- "Imputed"
SE$imputation[SE$quarter == 2 & SE$division == "23"] <- "Imputed"
SE$imputation[SE$quarter == 3 & SE$division == "23"] <- "Imputed"
SE$imputation[SE$quarter == 2 & SE$division == "24"] <- "Imputed"

c01 <- bind_rows(PL, DE, DK, SE)

rm(PL, DE, DK, SE)

summarise(group_by(subset(c01, wr == "8+"), year, division), ton = sum(catch_t, na.rm = T))
summarise(group_by(c01, year, division), canum = sum(canum, na.rm = T))

```

# 2002
```{r}
file <- "T_3-3-9_INT-herring_22-24_2002 with revised Swedish data.xls" 
# Fleet E and not fleet D is used - 
#  in the summary and report it looks like E become D, so this will be corrected in the end

sheet_names <- excel_sheets(path = paste0(path_in, file))

PL <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "22-24-Pl")
sum(unique(PL$catch_t))
PL$imputation[PL$quarter == 3 & PL$division == "24"] <- "Imputed"
PL$imputation[PL$quarter == 4 & PL$division == "24"] <- "Imputed"

DE <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "22-24- GE")
sum(unique(DE$catch_t))
DE$imputation <- NA
DE$imputation[DE$quarter == 1 & DE$division == "22"] <- "Imputed"
DE$imputation[DE$quarter == 2 & DE$division == "22"] <- "Imputed"
DE$imputation[DE$quarter == 3 & DE$division == "22"] <- "Imputed"
DE$imputation[DE$quarter == 4 & DE$division == "22"] <- "Imputed"
DE$imputation[DE$quarter == 3 & DE$division == "24"] <- "Imputed"

DK <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "22-24-DK")
sum(unique(DK$catch_t))
DK$imputation <- NA
DK$imputation[DK$quarter == 2 & DK$division == "23"] <- "Imputed"
DK$imputation[DK$quarter == 3 & DK$division == "23"] <- "Imputed"
DK$imputation[DK$quarter == 4 & DK$division == "24"] <- "Imputed"

SE <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "22-24-SE")
sum(unique(SE$catch_t))
SE$imputation[SE$quarter == 1 & SE$division == "23"] <- "Imputed"
SE$imputation[SE$quarter == 2 & SE$division == "23"] <- "Imputed"
SE$imputation[SE$quarter == 3 & SE$division == "23"] <- "Imputed"
SE$imputation[SE$quarter == 4 & SE$division == "23"] <- "Imputed"

c02 <- bind_rows(PL, DE, DK, SE)

rm(PL, DE, DK, SE)

summarise(group_by(subset(c02, wr == "8+"), year, division), ton = sum(catch_t, na.rm = T))
summarise(group_by(c02, year, division), canum = sum(canum, na.rm = T))

```
# 2003
```{r}
file <- "T_3-3-9_INT-herring_22-24_2003.xls" 
# Fleet E and not fleet D is used - 
#  in the summary and report it looks like E become D, so this will be corrected in the end

sheet_names <- excel_sheets(path = paste0(path_in, file))

PL <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "22-24-Pl")
sum(unique(PL$catch_t))

DE <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "22-24- GE")
sum(unique(DE$catch_t))
DE$imputation <- NA
DE$imputation[DE$quarter == 1 & DE$division == "22"] <- "Imputed"
DE$imputation[DE$quarter == 2 & DE$division == "22"] <- "Imputed"
DE$imputation[DE$quarter == 3 & DE$division == "22"] <- "Imputed"
DE$imputation[DE$quarter == 4 & DE$division == "22"] <- "Imputed"
DE$imputation[DE$quarter == 3 & DE$division == "24"] <- "Imputed"

DK <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "22-24-DK")
sum(unique(DK$catch_t))
DK$imputation <- NA
DK$imputation[DK$quarter == 1 & DK$division == "23"] <- "Imputed"
DK$imputation[DK$quarter == 2 & DK$division == "23"] <- "Imputed"
DK$imputation[DK$quarter == 3 & DK$division == "23"] <- "Imputed"
DK$imputation[DK$quarter == 3 & DK$division == "24"] <- "Imputed"
DK$imputation[DK$quarter == 4 & DK$division == "24"] <- "Imputed"

SE <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "22-24-SE")
sum(unique(SE$catch_t))
SE$imputation[SE$quarter == 1 & SE$division == "23"] <- "Imputed"
SE$imputation[SE$quarter == 2 & SE$division == "23"] <- "Imputed"
SE$imputation[SE$quarter == 3 & SE$division == "23"] <- "Imputed"
SE$imputation[SE$quarter == 4 & SE$division == "23"] <- "Imputed"

c03 <- bind_rows(PL, DE, DK, SE)

rm(PL, DE, DK, SE)

summarise(group_by(subset(c03, wr == "8+"), year, division), ton = sum(catch_t, na.rm = T))
summarise(group_by(c03, year, division), canum = sum(canum, na.rm = T))

```

# 2004
```{r}
file <- "T_3-3-9_INT-herring_22-24_2004.xls" 
# Fleet E and not fleet D is used - 
#  in the summary and report it looks like E become D, so this will be corrected in the end

sheet_names <- excel_sheets(path = paste0(path_in, file))

PL <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "22-24-Pl")
sum(unique(PL$catch_t))

DE <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "22-24- GE")
sum(unique(DE$catch_t))
DE$imputation <- NA
DE$imputation[DE$quarter == 1 & DE$division == "22"] <- "Imputed"
DE$imputation[DE$quarter == 2 & DE$division == "22"] <- "Imputed"
DE$imputation[DE$quarter == 3 & DE$division == "22"] <- "Imputed"
DE$imputation[DE$quarter == 4 & DE$division == "22"] <- "Imputed"
DE$imputation[DE$quarter == 3 & DE$division == "24"] <- "Imputed"

DK <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "22-24-DK")
sum(unique(DK$catch_t))
DK$imputation <- NA
DK$imputation[DK$quarter == 1 & DK$division == "23"] <- "Imputed"
DK$imputation[DK$quarter == 2 & DK$division == "23"] <- "Imputed"
DK$imputation[DK$quarter == 3 & DK$division == "23"] <- "Imputed"
DK$imputation[DK$quarter == 3 & DK$division == "24"] <- "Imputed"

SE <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "22-24-SE")
sum(unique(SE$catch_t))
SE$imputation[SE$quarter == 1 & SE$division == "23"] <- "Imputed"
SE$imputation[SE$quarter == 2 & SE$division == "23"] <- "Imputed"
SE$imputation[SE$quarter == 3 & SE$division == "23"] <- "Imputed"
SE$imputation[SE$quarter == 4 & SE$division == "23"] <- "Imputed"

c04 <- bind_rows(PL, DE, DK, SE)

rm(PL, DE, DK, SE)

summarise(group_by(subset(c04, wr == "8+"), year, division), ton = sum(catch_t, na.rm = T))
summarise(group_by(c04, year, division), canum = sum(canum, na.rm = T))

```

# 2005
```{r}
file <- "T_3-3-9_INT-herring_22-24_2005_ok.xls" 
# Fleet E and not fleet D is used - 
#  in the summary and report it looks like E become D, so this will be corrected in the end

sheet_names <- excel_sheets(path = paste0(path_in, file))

PL <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "22-24-Pl")
sum(unique(PL$catch_t))

DE <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "22-24- GE")
sum(unique(DE$catch_t))
DE$imputation <- NA
DE$imputation[DE$quarter == 1 & DE$division == "22"] <- "Imputed"
DE$imputation[DE$quarter == 2 & DE$division == "22"] <- "Imputed"
DE$imputation[DE$quarter == 3 & DE$division == "22"] <- "Imputed"
DE$imputation[DE$quarter == 4 & DE$division == "22"] <- "Imputed"
DE$imputation[DE$quarter == 3 & DE$division == "24"] <- "Imputed"

DK <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "22-24-DK")
sum(unique(DK$catch_t))
DK$imputation <- NA
DK$imputation[DK$quarter == 2 & DK$division == "23"] <- "Imputed"
DK$imputation[DK$quarter == 3 & DK$division == "23"] <- "Imputed"
DK$imputation[DK$quarter == 4 & DK$division == "23"] <- "Imputed"
DK$imputation[DK$quarter == 3 & DK$division == "24"] <- "Imputed"

SE <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "22-24-SE")
sum(unique(SE$catch_t))
SE$imputation[SE$quarter == 1 & SE$division == "23"] <- "Imputed"
SE$imputation[SE$quarter == 2 & SE$division == "23"] <- "Imputed"
SE$imputation[SE$quarter == 3 & SE$division == "23"] <- "Imputed"
SE$imputation[SE$quarter == 4 & SE$division == "23"] <- "Imputed"

c05 <- bind_rows(PL, DE, DK, SE)

rm(PL, DE, DK, SE)

summarise(group_by(subset(c05, wr == "8+"), year, division), ton = sum(catch_t, na.rm = T))
summarise(group_by(c05, year, division), canum = sum(canum, na.rm = T))

```

# 2006
Total CATON and CANUM checked against spread sheet: ok
Imputations checked against spread sheet and report if unclear: ok

```{r, eval = T}
file <- "T_3-3-9_INT-herring_22-24_2007.xls"

sheet_names <- excel_sheets(path = paste0(path_in, file))

PL <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "22-24-Pl")
sum(unique(PL$catch_t))

DE <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "22-24- GE")
sum(unique(DE$catch_t))
DE$imputation <- NA
DE$imputation[DE$quarter == 1 & DE$division == "22"] <- "DK, F, Q1, 22"
DE$imputation[DE$quarter == 2 & DE$division == "22"] <- "DK, F, Q1, 22"
DE$imputation[DE$quarter == 3 & DE$division == "22"] <- "DE, F, Q4, 24"
DE$imputation[DE$quarter == 4 & DE$division == "22"] <- "DE, F, Q4, 24"
DE$imputation[DE$quarter == 3 & DE$division == "24"] <- "DE, F, Q4, 24"

DK <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "22-24-DK")
sum(unique(DK$catch_t))
DK$imputation <- NA
DK$imputation[DK$quarter == 2 & DK$division == "22"] <- "DK, F, Q1, 22"
DK$imputation[DK$quarter == 3 & DK$division == "22"] <- "SE, F, Q3, 24"
DK$imputation[DK$quarter == 4 & DK$division == "22"] <- "SE, F, Q4, 24"
DK$imputation[DK$quarter == 1 & DK$division == "23"] <- "Imputed"
DK$imputation[DK$quarter == 2 & DK$division == "23"] <- "Imputed"
DK$imputation[DK$quarter == 3 & DK$division == "23"] <- "Imputed"
DK$imputation[DK$quarter == 4 & DK$division == "23"] <- "Imputed"
DK$imputation[DK$quarter == 1 & DK$division == "24"] <- "Imputed"

SE <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "22-24-SE")
sum(unique(SE$catch_t))
SE$imputation[SE$quarter == 1 & SE$division == "23"] <- "Imputed"
SE$imputation[SE$quarter == 3 & SE$division == "23"] <- "Imputed"
SE$imputation[SE$quarter == 4 & SE$division == "23"] <- "Imputed"

c06 <- bind_rows(PL, DE, DK, SE)

rm(PL, DE, DK, SE)

summarise(group_by(subset(c06, wr == "8+"), year, division), ton = sum(catch_t, na.rm = T))
summarise(group_by(c06, year, division), canum = sum(canum, na.rm = T))

```


# 2007

Total CATON and CANUM checked against spread sheet: ok

Imputations checked against spread sheet and report if unclear: ok
```{r, eval = T}
file <- "T_3-3-9_INT-herring_22-24_2007_other.xls"

sheet_names <- excel_sheets(path = paste0(path_in, file))

PL <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "22-24-Pl")
sum(unique(PL$catch_t))
PL$imputation <- NA

DE <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "22-24- GE")
sum(unique(DE$catch_t))
DE$imputation <- NA
DE$imputation[DE$quarter == 3 & DE$division == "22"] <- "DK, F, Q4, 22"
DE$imputation[DE$quarter == 4 & DE$division == "22"] <- "DK, F, Q4, 22"
DE$imputation[DE$quarter == 3 & DE$division == "24"] <- "DK, F, Q4, 24"

DK <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "22-24-DK")
sum(unique(DK$catch_t))
DK$imputation <- NA
DK$imputation[DK$quarter == 3 & DK$division == "23"] <- "KASU"
DK$imputation[DK$quarter == 4 & DK$division == "23"] <- "KASU"
DK$imputation[DK$quarter == 3 & DK$division == "24"] <- "DK, F, Q4, 24"

SE <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "22-24-SE")
sum(unique(SE$catch_t))
SE$imputation[SE$quarter == 3 & SE$division == "24"] <- "DK, F, Q4, 24"

c07 <- bind_rows(PL, DE, DK, SE)

rm(PL, DE, DK, SE)

summarise(group_by(subset(c07, wr == "8+"), year, division), ton = sum(catch_t, na.rm = T))
summarise(group_by(c07, year, division), canum = sum(canum, na.rm = T))

```


# 2008

Total CATON and CANUM checked against spread sheet: ok

Imputations checked against spread sheet and report if unclear: ok
```{r}
file <- "T_3-3-9_INT-herring_22-24_2008.xls"

sheet_names <- excel_sheets(path = paste0(path_in, file))

PL <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "22-24-Pl")
sum(unique(PL$catch_t))
PL$imputation <- NA
PL$imputation[PL$quarter == 3 & PL$division == "24"] <- "DK, F, Q4, 24"
PL$imputation[PL$quarter == 4 & PL$division == "24"] <- "DK, F, Q4, 24"

DE <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "22-24- GE")
sum(unique(DE$catch_t))
DE$imputation <- NA
DE$imputation[DE$quarter == 1 & DE$division == "22"] <- "DE, F, Q2, 22"
DE$imputation[DE$quarter == 3 & DE$division == "22"] <- "DK, F, Q4, 22"
DE$imputation[DE$quarter == 4 & DE$division == "22"] <- "DK, F, Q4, 22"
DE$imputation[DE$quarter == 3 & DE$division == "24"] <- "DE, F, Q4, 24"

DK <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "22-24-DK")
sum(unique(DK$catch_t))
DK$imputation <- NA
DK$imputation[DK$quarter == 4 & DK$division == "22"] <- "DK, F, Q3, 22"
DK$imputation[DK$quarter == 3 & DK$division == "23"] <- "DK, F, Q4, 23"
DK$imputation[DK$quarter == 2 & DK$division == "24"] <- "DK, F, Q1, 23"
DK$imputation[DK$quarter == 3 & DK$division == "24"] <- "DK, F, Q4, 23"

SE <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "22-24-SE")
sum(unique(SE$catch_t))
SE$imputation[SE$quarter == 2 & SE$division == "23"] <- "SE, F, Q2, 24"
SE$imputation[SE$quarter == 3 & SE$division == "23"] <- "SE, F, Q3, 24"
SE$imputation[SE$quarter == 4 & SE$division == "23"] <- "SE, F, Q4, 24"

c08 <- bind_rows(PL, DE, DK, SE)

rm(PL, DE, DK, SE)

summarise(group_by(subset(c08, wr == "8+"), year, division), ton = sum(catch_t, na.rm = T))
summarise(group_by(c08, year, division), canum = sum(canum, na.rm = T))

```

# 2009

Total CATON and CANUM checked against spread sheet: ok

Imputations checked against spread sheet and report if unclear: ok
```{r}
file <- "T_3-3-9_INT-herring_22-24_2009.xls"

sheet_names <- excel_sheets(path = paste0(path_in, file))

PL <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "22-24-Pl")
sum(unique(PL$catch_t))
PL$imputation <- NA
PL$imputation[PL$quarter == 3 & PL$division == "24"] <- "DK, F, Q3, 24"

DE <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "22-24- GE")
sum(unique(DE$catch_t))
DE$imputation <- NA
DE$imputation[DE$quarter == 3 & DE$division == "22"] <- "DK, F, Q3, 22"
DE$imputation[DE$quarter == 4 & DE$division == "22"] <- "DK, F, Q4, 22"
DE$imputation[DE$quarter == 3 & DE$division == "24"] <- "DE, F, Q4, 24"

DK <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "22-24-DK")
sum(unique(DK$catch_t))
DK$imputation <- NA
DK$imputation[DK$quarter == 2 & DK$division == "23"] <- "DK, F, Q1, 23"
DK$imputation[DK$quarter == 1 & DK$division == "24"] <- "DK, F, Q2, 23"
DK$imputation[DK$quarter == 3 & DK$division == "24"] <- "DK, F, Q4, 23"

SE <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "22-24-SE")
sum(unique(SE$catch_t))
SE$imputation[SE$quarter == 1 & SE$division == "23"] <- "SE, F, Q1, 24"
SE$imputation[SE$quarter == 3 & SE$division == "23"] <- "SE, F, Q4, 24"
SE$imputation[SE$quarter == 4 & SE$division == "23"] <- "SE, F, Q4, 24"
SE$imputation[SE$quarter == 2 & SE$division == "24"] <- "SE, F, Q1, 24"
SE$imputation[SE$quarter == 3 & SE$division == "24"] <- "SE, F, Q4, 24"

c09 <- bind_rows(PL, DE, DK, SE)

rm(PL, DE, DK, SE)

summarise(group_by(subset(c09, wr == "8+"), year, division), ton = sum(catch_t, na.rm = T))
summarise(group_by(c09, year, division), canum = sum(canum, na.rm = T))

```

# 2010

Total CATON and CANUM checked against spread sheet: ok

Imputations checked against spread sheet and report if unclear: ok
```{r}
file <- "T_3-3-9_INT-herring_22-24_2010.xls"

sheet_names <- excel_sheets(path = paste0(path_in, file))

PL <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "22-24-Pl")
sum(unique(PL$catch_t))
PL$imputation <- NA

DE <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "22-24- GE")
sum(unique(DE$catch_t))
DE$imputation <- NA

DK <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "22-24-DK")
sum(unique(DK$catch_t))
DK$imputation <- NA
DK$imputation[DK$quarter == 1 & DK$division == "23"] <- "DK, F, Q1, 22"
DK$imputation[DK$quarter == 2 & DK$division == "23"] <- "DK, F, Q1, 23"
DK$imputation[DK$quarter == 3 & DK$division == "24"] <- "DE, F, Q3, 23"
DK$imputation[DK$quarter == 4 & DK$division == "24"] <- "DE, F, Q4, 23"

SE <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "22-24-SE")
sum(unique(SE$catch_t))
SE$imputation[SE$quarter == 1 & SE$division == "23"] <- "SE, F, Q1, 24"
SE$imputation[SE$quarter == 3 & SE$division == "23"] <- "SE, F, Q4, 24"
SE$imputation[SE$quarter == 4 & SE$division == "23"] <- "SE, F, Q4, 24"
SE$imputation[SE$quarter == 3 & SE$division == "24"] <- "SE, F, Q4, 24"

c10 <- bind_rows(PL, DE, DK, SE)

rm(PL, DE, DK, SE)

summarise(group_by(subset(c10, wr == "8+"), year, division), ton = sum(catch_t, na.rm = T))
summarise(group_by(c10, year, division), canum = sum(canum, na.rm = T))

```

# 2011

Total CATON and CANUM checked against spread sheet: ok

Imputations checked against spread sheet and report if unclear: ok
```{r}
file <- "T_3-3-9_INT-herring_22-24_2011.xls"

sheet_names <- excel_sheets(path = paste0(path_in, file))

PL <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "22-24-Pl")
sum(unique(PL$catch_t))
PL$imputation <- NA

DE <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "22-24- GE")
sum(unique(DE$catch_t))
DE$imputation <- NA

DK <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "22-24-DK")
sum(unique(DK$catch_t))
DK$imputation <- NA
DK$imputation[DK$quarter == 3 & DK$division == "22"] <- "DK, F, Q4, 22"
DK$imputation[DK$quarter == 1 & DK$division == "23"] <- "DK, F, Q1, 22"
DK$imputation[DK$quarter == 2 & DK$division == "23"] <- "DK, F, Q1, 22"
DK$imputation[DK$quarter == 3 & DK$division == "23"] <- "DK, F, Q4, 22"
DK$imputation[DK$quarter == 4 & DK$division == "23"] <- "DK, F, Q4, 22"
DK$imputation[DK$quarter == 1 & DK$division == "24"] <- "DK, F, Q1, 24"
DK$imputation[DK$quarter == 2 & DK$division == "24"] <- "DE, F, Q2, 24"
DK$imputation[DK$quarter == 3 & DK$division == "24"] <- "DE, F, Q3, 24"
DK$imputation[DK$quarter == 4 & DK$division == "24"] <- "DE, F, Q4, 24"

SE <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "22-24-SE")
sum(unique(SE$catch_t))
SE$imputation[SE$quarter == 1 & SE$division == "23"] <- "SE, F, Q1, 24"
SE$imputation[SE$quarter == 2 & SE$division == "23"] <- "SE, F, Q1, 24"
SE$imputation[SE$quarter == 3 & SE$division == "23"] <- "SE, F, Q4, 24"
SE$imputation[SE$quarter == 4 & SE$division == "23"] <- "SE, F, Q4, 24"
SE$imputation[SE$quarter == 2 & SE$division == "24"] <- "SE, F, Q1, 24"
SE$imputation[SE$quarter == 3 & SE$division == "24"] <- "SE, F, Q4, 24"

c11 <- bind_rows(PL, DE, DK, SE)

rm(PL, DE, DK, SE)

summarise(group_by(subset(c11, wr == "8+"), year, division), ton = sum(catch_t, na.rm = T))
summarise(group_by(c11, year, division), canum = sum(canum, na.rm = T))

```

# 2012

Total CATON and CANUM checked against spread sheet: ok
Imputations checked against spread sheet and report if unclear: ok
```{r}
file <- "T_3-3-9_INT-herring_22-24_2012.xls"

sheet_names <- excel_sheets(path = paste0(path_in, file))

PL <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "22-24-Pl")
sum(unique(PL$catch_t))
PL$imputation <- NA

DE <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "22-24- GE")
sum(unique(DE$catch_t))
DE$imputation <- NA

DK <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "22-24-DK")
sum(unique(DK$catch_t))
DK$imputation <- NA
DK$imputation[DK$quarter == 2 & DK$division == "22"] <- "DK, F, Q1, 22"
DK$imputation[DK$quarter == 3 & DK$division == "22"] <- "DK, F, Q4, 22"
DK$imputation[DK$quarter == 2 & DK$division == "23"] <- "DK, F, Q1, 23"
DK$imputation[DK$quarter == 3 & DK$division == "23"] <- "DK, F, Q4, 23"
DK$imputation[DK$quarter == 2 & DK$division == "24"] <- "DK, F, Q1, 24"
DK$imputation[DK$quarter == 3 & DK$division == "24"] <- "DK, F, Q4, 24"

SE <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "22-24-SE")
sum(unique(SE$catch_t))
SE$imputation[SE$quarter == 1 & SE$division == "23"] <- "SE, F, Q1, 24"
SE$imputation[SE$quarter == 3 & SE$division == "23"] <- "SE, F, Q4, 24"
SE$imputation[SE$quarter == 4 & SE$division == "23"] <- "SE, F, Q4, 24"
SE$imputation[SE$quarter == 3 & SE$division == "24"] <- "SE, F, Q4, 24"

c12 <- bind_rows(PL, DE, DK, SE)

rm(PL, DE, DK, SE)

summarise(group_by(subset(c12, wr == "8+"), year, division), ton = sum(catch_t, na.rm = T))
summarise(group_by(c12, year, division), canum = sum(canum, na.rm = T))

```

# 2013

Total CATON and CANUM checked against spread sheet: ok
Imputations checked against spread sheet and report if unclear: ok
```{r}
file <- "T_3-3-9_INT-herring_22-24_2013.xls"

sheet_names <- excel_sheets(path = paste0(path_in, file))

PL <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "22-24-Pl")
sum(unique(PL$catch_t))
PL$imputation <- NA

DE <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "22-24- GE")
sum(unique(DE$catch_t))
DE$imputation <- NA

DK <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "22-24-DK")
sum(unique(DK$catch_t))
DK$imputation <- NA
DK$imputation[DK$quarter == 1 & DK$division == "23"] <- "DK, F, Q1, 24"
DK$imputation[DK$quarter == 2 & DK$division == "23"] <- "DK, F, Q2, 24"
DK$imputation[DK$quarter == 3 & DK$division == "23"] <- "DK, F, Q3, 24"
DK$imputation[DK$quarter == 4 & DK$division == "23"] <- "DK, F, Q4, 24"

SE <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "22-24-SE")
sum(unique(SE$catch_t))
SE$imputation[SE$quarter == 1 & SE$division == "23"] <- "SE, F, Q1, 24"
SE$imputation[SE$quarter == 3 & SE$division == "23"] <- "SE, F, Q4, 24"
SE$imputation[SE$quarter == 4 & SE$division == "23"] <- "SE, F, Q4, 24"
SE$imputation[SE$quarter == 2 & SE$division == "24"] <- "SE, F, Q1, 24"
SE$imputation[SE$quarter == 3 & SE$division == "24"] <- "SE, F, Q4, 24"

c13 <- bind_rows(PL, DE, DK, SE)

rm(PL, DE, DK, SE)

summarise(group_by(subset(c13, wr == "8+"), year, division), ton = sum(catch_t, na.rm = T))
summarise(group_by(c13, year, division), canum = sum(canum, na.rm = T))

```

# 2014
Total CATON and CANUM checked against spread sheet: ok
Imputations checked against spread sheet and report if unclear: ok
```{r}
file <- "Copy of T_3-3-9_INT-herring_22-24_2014_corrected.xls"

sheet_names <- excel_sheets(path = paste0(path_in, file))

PL <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "22-24-Pl")
sum(unique(PL$catch_t))
PL$imputation <- NA

DE <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "22-24- GE")
sum(unique(DE$catch_t))
DE$imputation <- NA

DK <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "22-24-DK")
sum(unique(DK$catch_t))
DK$imputation <- NA
DK$imputation[DK$quarter == 2 & DK$division == "22"] <- "DK, F, Q1, 22"
DK$imputation[DK$quarter == 3 & DK$division == "22"] <- "DK, F, Q4, 22"
DK$imputation[DK$quarter == 2 & DK$division == "23"] <- "DK, F, Q1, 23"
DK$imputation[DK$quarter == 4 & DK$division == "24"] <- "DK, F, Q3, 24"

SE <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "22-24-SE")
sum(unique(SE$catch_t))
SE$imputation[SE$quarter == 1 & SE$division == "23"] <- "SE, F, Q1, 24"
SE$imputation[SE$quarter == 3 & SE$division == "23"] <- "SE, F, Q4, 24"
SE$imputation[SE$quarter == 4 & SE$division == "23"] <- "SE, F, Q4, 24"

c14 <- bind_rows(PL, DE, DK, SE)

rm(PL, DE, DK, SE)

summarise(group_by(subset(c14, wr == "8+"), year, division), ton = sum(catch_t, na.rm = T))
summarise(group_by(c14, year, division), canum = sum(canum, na.rm = T))

```
# 2015
Total CATON and CANUM checked against spread sheet: ok
Imputations checked against spread sheet and report if unclear: ok
```{r}
file <- "T_3-3-9_INT-herring_22-24_2015.xls"

sheet_names <- excel_sheets(path = paste0(path_in, file))

PL <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "22-24-Pl")
sum(unique(PL$catch_t))
PL$imputation <- NA

DE <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "22-24- GE")
sum(unique(DE$catch_t))
DE$imputation <- NA

DK <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "22-24-DK")
sum(unique(DK$catch_t))
DK$imputation <- NA
DK$imputation[DK$quarter == 2 & DK$division == "22"] <- "DK, F, Q1, 22"
DK$imputation[DK$quarter == 3 & DK$division == "22"] <- "DK, F, Q4, 22"
DK$imputation[DK$quarter == 2 & DK$division == "23"] <- "DK, F, Q2, 24"
DK$imputation[DK$quarter == 3 & DK$division == "23"] <- "DK, F, Q4, 24"
DK$imputation[DK$quarter == 4 & DK$division == "23"] <- "DK, F, Q4, 24"
DK$imputation[DK$quarter == 3 & DK$division == "24"] <- "DE, F, Q4, 24"
DK$imputation[DK$quarter == 4 & DK$division == "24"] <- "DE, F, Q4, 24"

SE <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "22-24-SE")
sum(unique(SE$catch_t))
SE$imputation[SE$quarter == 3 & SE$division == "22"] <- "SE, F, Q4, 24"
SE$imputation[SE$quarter == 1 & SE$division == "23"] <- "DK, F, Q1, 22"
SE$imputation[SE$quarter == 2 & SE$division == "23"] <- "SE, F, Q1, 24"
SE$imputation[SE$quarter == 3 & SE$division == "23"] <- "SE, F, Q4, 24"
SE$imputation[SE$quarter == 4 & SE$division == "23"] <- "SE, F, Q4, 24"
SE$imputation[SE$quarter == 2 & SE$division == "24"] <- "SE, F, Q1, 24"
SE$imputation[SE$quarter == 3 & SE$division == "24"] <- "SE, F, Q4, 24"

c15 <- bind_rows(PL, DE, DK, SE)

rm(PL, DE, DK, SE)

summarise(group_by(subset(c15, wr == "8+"), year, division), ton = sum(catch_t, na.rm = T))
summarise(group_by(c15, year, division), canum = sum(canum, na.rm = T))

```

# Combine
```{r}

dat <- bind_rows(c00, c01, c02, c03, c04, c05, c06, c07, c08, c09, c10, c11, c12, c13, c14, c15)
rm(c00, c01, c02, c03, c04, c05, c06, c07, c08, c09, c10, c11, c12, c13, c14, c15)
unique(dat$year)
unique(dat$ctry)
unique(dat$division)

# Clean up codes
dat$area <- NA
dat$area[dat$division == "22"] <- "27.3.c.22"
dat$area[dat$division == "23"] <- "27.3.b.23"
dat$area[dat$division == "24"] <- "27.3.d.24"

dat$ctry[dat$ctry == "DK"] <- "Denmark"
dat$ctry[dat$ctry == "Faroee"] <- "Faroe Islands"
dat$ctry[dat$ctry == "NLD"] <- "Nedtherlands"


dat$weca <- as.numeric(dat$weca)
dat$canum <- as.numeric(dat$canum)
dat$canum_1000 <- dat$canum * 1000
dat$weca_g <- dat$weca

# add all wr

head <- distinct(dat, ctry, year, quarter, fleet, area, catch_t)
wr <- distinct(subset(dat, !is.na(wr)), wr)
full_wr <- cross_join(head, wr)

dat_full_wr <- left_join(full_wr, dat)
dat_full_wr$canum_1000[is.na(dat_full_wr$canum_1000)] <- 0

dat <- dat_full_wr
```

# Output
```{r}

write.table(dat, paste0(path_data, "old_canum_with_imputations_2000_2015_22-24.csv"), row.names = F, sep = ";")

```

