---
title: "read_in"
author: "Kirsten Birch Håkansson, DTU Aqua"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = F, message = F)

library(readxl)
library(dplyr)

source("../utils/read_canum_sheet_old_format_IIIa.R")

path_in <- "../boot/data/historical_data/sc_sheets_old_format/"

```

# 2000
Total CATON and CANUM checked against Thomas figures: not sure NOR has been excluded in Thomas figures
Total CATON and CANUM checked against report: Don't match - Norway has been excluded
Total CATON and CANUM checked against spread sheet: ok
Imputations checked against spread sheet and report if unclear: ok
```{r, eval = T}
# file <- "HER-IIIa-2000-revised ex-Norway.xls" 
file <- "HER-IIIa-2000-revised.xls" 
# file <- "HER-IIIa-2000.xls" 
# Fleet E and not fleet D is used - 
#  in the summary and report it looks like E become D, so this will be corrected in the end

sheet_names <- excel_sheets(path = paste0(path_in, file))


SD20NO <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD20-NO") 
sum(unique(SD20NO$catch_t))
SD20NO$imputation <- NA
SD20NO$imputation[SD20NO$quarter == 3 & SD20NO$fleet == "C"] <- "SE, C, Q3, 20"
SD20NO$imputation[SD20NO$quarter == 4 & SD20NO$fleet == "C"] <- "SE, C, Q4, 20"

SD20SE <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD20-SE") 
sum(unique(SD20SE$catch_t))
SD20SE$imputation <- NA
SD20SE$imputation[SD20SE$quarter == 2 & SD20SE$fleet == "E"] <- "DK, E, Q2, 20"

SD20DK <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD20-DK")
sum(unique(SD20DK$catch_t))
SD20DK$imputation <- NA
SD20DK$imputation[SD20DK$quarter == 1 & SD20DK$fleet == "C"] <- "SE, C, Q1, 20"
SD20DK$imputation[SD20DK$quarter == 2 & SD20DK$fleet == "C"] <- "SE, C, Q2, 20"

SD21SE <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD21-SE")
sum(unique(SD21SE$catch_t))
SD21SE$imputation <- NA
SD21SE$imputation <- NA
SD21SE$imputation[SD21SE$quarter == 1 & SD21SE$fleet == "E"] <- "DK, E, Q1, 21"
SD21SE$imputation[SD21SE$quarter == 3 & SD21SE$fleet == "E"] <- "DK, E, Q1, 21"
SD21SE$imputation[SD21SE$quarter == 4 & SD21SE$fleet == "E"] <- "DK, E, Q3, 20"

SD21DK <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD21-DK")
sum(unique(SD21DK$catch_t))
SD21DK$imputation <- NA
SD21DK$imputation[SD21DK$quarter == 2 & SD21DK$fleet == "E"] <- "DK, E, Q1, 21"
SD21DK$imputation[SD21DK$quarter == 3 & SD21DK$fleet == "E"] <- "DK, E, Q3, 21"


c00 <- bind_rows(SD20NO, SD20DK, SD20SE, SD21DK, SD21SE)

# Rename fleet E to D
c00 <- subset(c00, fleet != "D")
c00$fleet[c00$fleet == "E"] <- "D"

rm(SD20NO, SD20DK, SD20SE, SD21DK, SD21SE)

summarise(group_by(subset(c00, wr == "8+"), year, division), ton = sum(catch_t, na.rm = T))
summarise(group_by(c00, year, division), canum = sum(canum, na.rm = T))

```

# 2001
Total CATON and CANUM checked against Thomas figures: CANUM ok. CATON not ok
Total CATON and CANUM checked against original report: Don't match - Norway has been excluded
Total CATON and CANUM checked against spread sheet: ok
Imputations checked against spread sheet and report if unclear: ok
```{r, eval = T}
file <- "HER-IIIa-2001-revised ex- Norway.xls"

# Fleet E and not fleet D is used - 
#  in the summary and report it looks like E become D, so this will be corrected in the end

sheet_names <- excel_sheets(path = paste0(path_in, file))

SD20SE <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD20-SE") 
sum(unique(SD20SE$catch_t))
SD20SE$imputation <- NA
SD20SE$imputation[SD20SE$quarter == 2 & SD20SE$fleet == "E"] <- "DK, E, Q2, 20"
SD20SE$imputation[SD20SE$quarter == 3 & SD20SE$fleet == "E"] <- "DK, E, Q3, 20"
SD20SE$imputation[SD20SE$quarter == 4 & SD20SE$fleet == "E"] <- "DK, E, Q4, 20"

SD20DK <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD20-DK")
sum(unique(SD20DK$catch_t))
SD20DK$imputation <- NA
SD20DK$imputation[SD20DK$quarter == 2 & SD20DK$fleet == "C"] <- "DK, C, Q1, 20"

SD21SE <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD21-SE")
sum(unique(SD21SE$catch_t))
SD21SE$imputation <- NA
SD21SE$imputation[SD21SE$quarter == 3 & SD21SE$fleet == "C"] <- "DK, C, Q3, 21"

SD21DK <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD21-DK")
sum(unique(SD21DK$catch_t))
SD21DK$imputation <- NA
SD21DK$imputation[SD21DK$quarter == 2 & SD21DK$fleet == "C"] <- "SE, C, Q2, 21"


c01 <- bind_rows(SD20DK, SD20SE, SD21DK, SD21SE)

# Rename fleet E to D
c01 <- subset(c01, fleet != "D")
c01$fleet[c01$fleet == "E"] <- "D"

rm(SD20DK, SD20SE, SD21DK, SD21SE)

summarise(group_by(subset(c01, wr == "8+"), year, division), ton = sum(catch_t, na.rm = T))
summarise(group_by(c01, year, division), canum = sum(canum, na.rm = T))

```

# 2002
Total CATON and CANUM checked against Thomas figures: ok
Total CATON and CANUM checked against report: ok
Total CATON and CANUM checked against spread sheet: ok
Imputations checked against spread sheet and report if unclear: ok
```{r, eval = T}
file <- "HER-IIIa-2002-with revised Swedish data.xls" 
# Fleet E and not fleet D is used - 
#  in the summary and report it looks like E become D, so this will be corrected in the end

sheet_names <- excel_sheets(path = paste0(path_in, file))

SD20SE <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD20-SE") 
sum(unique(SD20SE$catch_t))
SD20SE$imputation <- NA
SD20SE$imputation[SD20SE$quarter == 2 & SD20SE$fleet == "E"] <- "DK, E, Q2, 20"
SD20SE$imputation[SD20SE$quarter == 3 & SD20SE$fleet == "E"] <- "DK, E, Q3, 20"
SD20SE$imputation[SD20SE$quarter == 4 & SD20SE$fleet == "E"] <- "DK, E, Q4, 20"

SD20DK <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD20-DK")
sum(unique(SD20DK$catch_t))
SD20DK$imputation <- NA

SD21SE <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD21-SE")
sum(unique(SD21SE$catch_t))
SD21SE$imputation <- NA
SD21SE$imputation <- NA
SD21SE$imputation[SD21SE$quarter == 1 & SD21SE$fleet == "E"] <- "DK, E, Q1, 21"
SD21SE$imputation[SD21SE$quarter == 4 & SD21SE$fleet == "E"] <- "DK, E, Q3, 21"

SD21DK <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD21-DK")
sum(unique(SD21DK$catch_t))
SD21DK$imputation <- NA
SD21DK$imputation[SD21DK$quarter == 2 & SD21DK$fleet == "C"] <- "SE, C, Q2, 21"


c02 <- bind_rows(SD20DK, SD20SE, SD21DK, SD21SE)

# Rename fleet E to D
c02 <- subset(c02, fleet != "D")
c02$fleet[c02$fleet == "E"] <- "D"

rm(SD20DK, SD20SE, SD21DK, SD21SE)

summarise(group_by(subset(c02, wr == "8+"), year, division), ton = sum(catch_t, na.rm = T))
summarise(group_by(c02, year, division), canum = sum(canum, na.rm = T))

```

# 2003
Total CATON and CANUM checked against Thomas figures: CANUM ok. CATON differs
Total CATON and CANUM checked against report: ok
Total CATON and CANUM checked against spread sheet: ok - an error in the spread sheet has been corrected for SD21DK
Imputations checked against spread sheet and report if unclear: ok
```{r, eval = T}
file <- "HER-IIIa-2003 revised 110304.xls" 
# Fleet E and not fleet D is used - 
#  in the summary and report it looks like E become D, so this will be corrected in the end

sheet_names <- excel_sheets(path = paste0(path_in, file))

SD20SE <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD20-SE") 
sum(unique(SD20SE$catch_t))
SD20SE$imputation <- NA
SD20SE$imputation[SD20SE$quarter == 2 & SD20SE$fleet == "E"] <- "DK, C, Q2, 20"
SD20SE$imputation[SD20SE$quarter == 3 & SD20SE$fleet == "E"] <- "DK, C, Q3, 20"

SD20DK <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD20-DK")
sum(unique(SD20DK$catch_t))
SD20DK$imputation <- NA
SD20DK$imputation[SD20DK$quarter == 2 & SD20DK$fleet == "C"] <- "DK, C, Q1, 20"
SD20DK$imputation[SD20DK$quarter == 2 & SD20DK$fleet == "E"] <- "DK, E, Q1, 20"

SD20DE <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD20-OTH")
sum(unique(SD20DE$catch_t))
SD20DE$imputation <- NA
SD20DE$imputation[SD20DE$quarter == 3 & SD20DE$fleet == "C"] <- "DK, C, Q3, 20"
SD20DE$imputation[SD20DE$quarter == 4 & SD20DE$fleet == "C"] <- "DK, C, Q4, 20"

SD21SE <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD21-SE")
sum(unique(SD21SE$catch_t))
SD21SE$imputation <- NA
SD21SE$imputation <- NA
SD21SE$imputation[SD21SE$quarter == 1 & SD21SE$fleet == "E"] <- "DK, C, Q1, 21"
SD21SE$imputation[SD21SE$quarter == 2 & SD21SE$fleet == "E"] <- "DK, C, Q2, 21"
SD21SE$imputation[SD21SE$quarter == 3 & SD21SE$fleet == "C"] <- "DK, E, Q3, 21"

SD21DK <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD21-DK")
sum(unique(SD21DK$catch_t))
SD21DK$imputation <- NA

c03 <- bind_rows(SD20DE, SD20DK, SD20SE, SD21DK, SD21SE)

# Rename fleet E to D
c03 <- subset(c03, fleet != "D")
c03$fleet[c03$fleet == "E"] <- "D"

rm(SD20DE, SD20DK, SD20SE, SD21DK, SD21SE)

summarise(group_by(subset(c03, wr == "8+"), year, division), ton = sum(catch_t, na.rm = T))
summarise(group_by(c03, year, division), canum = sum(canum, na.rm = T))

```

# 2004
Total CATON and CANUM checked against Thomas figures: ok
Total CATON and CANUM checked against report: ok
Total CATON and CANUM checked against spread sheet: ok - an error in the spread sheet has been corrected for SD21DK
Imputations checked against spread sheet and report if unclear: ok
```{r, eval = T}
file <- "HER-IIIa-2004.xls" 
# Fleet E and not fleet D is used - 
#  in the summary and report it looks like E become D, so this will be corrected in the end

sheet_names <- excel_sheets(path = paste0(path_in, file))

SD20NO <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD20-NO")
sum(unique(SD20NO$catch_t))
SD20NO$imputation <- NA
SD20NO$imputation[SD20NO$quarter == 1 & SD20NO$fleet == "C"] <- "DK, C, Q1, 20"
SD20NO$imputation[SD20NO$quarter == 3 & SD20NO$fleet == "C"] <- "DK, C, Q3, 20"
SD20NO$imputation[SD20NO$quarter == 4 & SD20NO$fleet == "C"] <- "DK, C, Q3, 20"

SD20SE <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD20-SE") 
sum(unique(SD20SE$catch_t))
SD20SE$imputation <- NA
SD20SE$imputation[SD20SE$quarter == 2 & SD20SE$fleet == "C"] <- "DK, C, Q2, 4ae"
SD20SE$imputation[SD20SE$quarter == 3 & SD20SE$fleet == "C"] <- "DK, C, Q3, 20"

SD20DK <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD20-DK")
sum(unique(SD20DK$catch_t))
SD20DK$imputation <- NA
SD20DK$imputation[SD20DK$quarter == 2 & SD20DK$fleet == "C"] <- "DK, C, Q2, 4ae"

SD20DE <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD20-OTH")
sum(unique(SD20DE$catch_t))
SD20DE$imputation <- NA
SD20DE$imputation[SD20DE$quarter == 3 & SD20DE$fleet == "C"] <- "DK, C, Q3, 20"

SD21SE <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD21-SE")
sum(unique(SD21SE$catch_t))
SD21SE$imputation <- NA
SD21SE$imputation[SD21SE$quarter == 4 & SD21SE$fleet == "E"] <- "DK, E, Q4, 21"

SD21DK <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD21-DK")
sum(unique(SD21DK$catch_t))
SD21DK$imputation <- NA

c04 <- bind_rows(SD20NO, SD20DE, SD20DK, SD20SE, SD21DK, SD21SE)

# Rename fleet E to D
c04 <- subset(c04, fleet != "D")
c04$fleet[c04$fleet == "E"] <- "D"

rm(SD20NO, SD20DE, SD20DK, SD20SE, SD21DK, SD21SE)

summarise(group_by(subset(c04, wr == "8+"), year, division), ton = sum(catch_t, na.rm = T))
summarise(group_by(c04, year, division), canum = sum(canum, na.rm = T))

```

# 2005
Total CATON and CANUM checked against Thomas figures: ok
Total CATON and CANUM checked against original report: ok
Total CATON and CANUM checked against spread sheet: ok
Imputations checked against spread sheet and report if unclear: ok
```{r}
file <- "HER-IIIa-2005_ok.xls" 
# Fleet E and not fleet D is used - 
#  in the summary and report it looks like E become D, so this will be corrected in the end

sheet_names <- excel_sheets(path = paste0(path_in, file))

SD20SE <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD20-SE")
sum(unique(SD20SE$catch_t))
SD20SE$imputation <- NA
SD20SE$imputation[SD20SE$quarter == 3 & SD20SE$fleet == "E"] <- "DK, E, Q3, 20"

SD20DK <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD20-DK")
sum(unique(SD20DK$catch_t))
SD20DK$imputation <- NA
SD20DK$imputation[SD20DK$quarter == 1 & SD20DK$fleet == "C"] <- "SE, C, Q1, 20"
SD20DK$imputation[SD20DK$quarter == 2 & SD20DK$fleet == "C"] <- "SE, C, Q2, 20"
SD20DK$imputation[SD20DK$quarter == 1 & SD20DK$fleet == "E"] <- "SE, E, Q1, 20"

SD20DE <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD20-OTH")
sum(unique(SD20DE$catch_t))
SD20DE$imputation <- NA
SD20DE$imputation[SD20DE$quarter == 3 & SD20DE$fleet == "C"] <- "DK, C, Q3, 20"
SD20DE$imputation[SD20DE$quarter == 4 & SD20DE$fleet == "C"] <- "DK, C, Q4, 20"

SD20FO <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD20-OTH (2)")
sum(unique(SD20FO$catch_t))
SD20FO$imputation <- NA
SD20FO$imputation[SD20FO$quarter == 3 & SD20FO$fleet == "E"] <- "DK, E, Q3, 20"
SD20FO$imputation[SD20FO$quarter == 4 & SD20FO$fleet == "E"] <- "DK, E, Q4, 20"

SD21SE <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD21-SE")
sum(unique(SD21SE$catch_t))
SD21SE$imputation <- NA
SD21SE$imputation <- NA
SD21SE$imputation[SD21SE$quarter == 1 & SD21SE$fleet == "E"] <- "DK, E, Q1, 21"
SD21SE$imputation[SD21SE$quarter == 3 & SD21SE$fleet == "E"] <- "DK, E, Q3, 21"
SD21SE$imputation[SD21SE$quarter == 4 & SD21SE$fleet == "E"] <- "DK, E, Q4, 21"

SD21DK <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD21-DK")
sum(unique(SD21DK$catch_t))
SD21DK$imputation <- NA
SD21DK$imputation[SD21DK$quarter == 2 & SD21DK$fleet == "C"] <- "SE, C, Q2, 21"
SD21DK$imputation[SD21DK$quarter == 3 & SD21DK$fleet == "C"] <- "SE, C, Q3, 21"


c05 <- bind_rows(SD20DE, SD20DK, SD20FO, SD20SE, SD21DK, SD21SE)

# Rename fleet E to D
c05 <- subset(c05, fleet != "D")
c05$fleet[c05$fleet == "E"] <- "D"

rm(SD20DE, SD20DK, SD20FO, SD20SE, SD21DK, SD21SE)

summarise(group_by(subset(c05, wr == "8+"), year, division), ton = sum(catch_t, na.rm = T))
summarise(group_by(c05, year, division), canum = sum(canum, na.rm = T))

```

# 2006
Total CATON and CANUM checked against Thomas figures: CANUM ok, but CATON too high in and it looks like Kattegat and Skagerrak are swapped
Total CATON and CANUM checked against original report: ok
Total CATON and CANUM checked against spread sheet: ok
Imputations checked against spread sheet and report if unclear: ok
```{r}
file <- "HER-IIIa-2006.xls" 

sheet_names <- excel_sheets(path = paste0(path_in, file))

SD20SE <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD20-SE") 
sum(unique(SD20SE$catch_t))
SD20SE$imputation <- NA
SD20SE$imputation[SD20SE$quarter == 1 & SD20SE$fleet == "D"] <- "SE, C, Q1, 20"
SD20SE$imputation[SD20SE$quarter == 2 & SD20SE$fleet == "D"] <- "SE, C, Q2, 20"
SD20SE$imputation[SD20SE$quarter == 3 & SD20SE$fleet == "D"] <- "SE, C, Q3, 20"
SD20SE$imputation[SD20SE$quarter == 4 & SD20SE$fleet == "D"] <- "SE, C, Q4, 20"

SD20DK <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD20-DK")
sum(unique(SD20DK$catch_t))
SD20DK$imputation <- NA
SD20DK$imputation[SD20DK$quarter == 4 & SD20DK$fleet == "C"] <- "SE, C, Q4, 20"
SD20DK$imputation[SD20DK$quarter == 4 & SD20DK$fleet == "D"] <- "SE, C, Q4, 20"

SD20DE <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD20-OTH")
sum(unique(SD20DE$catch_t))
SD20DE$imputation <- NA
SD20DE$imputation[SD20DE$quarter == 3 & SD20DE$fleet == "C"] <- "DK, C, Q3, 20"

SD21SE <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD21-SE")
sum(unique(SD21SE$catch_t))
SD21SE$imputation <- NA
SD21SE$imputation[SD21SE$quarter == 1 & SD21SE$fleet == "D"] <- "SE, C, Q1, 21"
SD21SE$imputation[SD21SE$quarter == 3 & SD21SE$fleet == "D"] <- "SE, C, Q3, 21"
SD21SE$imputation[SD21SE$quarter == 4 & SD21SE$fleet == "D"] <- "SE, C, Q4, 21"

SD21DK <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD21-DK")
sum(unique(SD21DK$catch_t))
SD21DK$imputation <- NA
SD21DK$imputation[SD21DK$quarter == 2 & SD21DK$fleet == "D"] <- "DK, D, Q1, 21"


c06 <- bind_rows(SD20DE, SD20DK, SD20SE, SD21DK, SD21SE)

rm(SD20DE, SD20DK, SD20SE, SD21DK, SD21SE)

summarise(group_by(subset(c06, wr == "8+"), year, division), ton = sum(catch_t, na.rm = T))
summarise(group_by(c06, year, division), canum = sum(canum, na.rm = T))

```

# 2007
Total CATON and CANUM checked against Thomas figures: ok
Total CATON and CANUM checked against original report: ok 
Total CATON and CANUM checked against spread sheet: ok
Imputations checked against spread sheet and report if unclear: ok
```{r}
file <- "HER-IIIa-2007new.xls"

sheet_names <- excel_sheets(path = paste0(path_in, file))

SD20NO <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD20-NO")
sum(unique(SD20NO$catch_t))
SD20NO$imputation <- NA
SD20NO$imputation[SD20NO$quarter == 1 & SD20NO$fleet == "C"] <- "DK, C, Q2, 20"
SD20NO$imputation[SD20NO$quarter == 2 & SD20NO$fleet == "C"] <- "DK, C, Q2, 20"
SD20NO$imputation[SD20NO$quarter == 3 & SD20NO$fleet == "C"] <- "DK, C, Q3, 20"
SD20NO$imputation[SD20NO$quarter == 4 & SD20NO$fleet == "C"] <- "DK, C, Q3, 20"

SD20SE <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD20-SE")
sum(unique(SD20SE$catch_t))
SD20SE$imputation <- NA
SD20SE$imputation[SD20SE$quarter == 1 & SD20SE$fleet == "D"] <- "SE, C, Q1, 20"
SD20SE$imputation[SD20SE$quarter == 2 & SD20SE$fleet == "D"] <- "SE, C, Q2, 20"
SD20SE$imputation[SD20SE$quarter == 3 & SD20SE$fleet == "D"] <- "SE, C, Q3, 20"
SD20SE$imputation[SD20SE$quarter == 4 & SD20SE$fleet == "D"] <- "SE, C, Q4, 20"

SD20DK <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD20-DK")
sum(unique(SD20DK$catch_t))
SD20DK$imputation <- NA
SD20DK$imputation[SD20DK$quarter == 2 & SD20DK$fleet == "D"] <- "DK, D, Q1, 21"
SD20DK$imputation[SD20DK$quarter == 4 & SD20DK$fleet == "D"] <- "DK, D, Q4, 21"
SD20DK$imputation[SD20DK$quarter == 4 & SD20DK$fleet == "C"] <- "DK, C, Q3, 20"

SD20DE <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD20-OTH")
sum(unique(SD20DE$catch_t))

SD21SE <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD21-SE")
sum(unique(SD21SE$catch_t))
SD21SE$imputation <- NA
SD21SE$imputation[SD21SE$quarter == 1 & SD21SE$fleet == "D"] <- "SE, C, Q1, 21"
SD21SE$imputation[SD21SE$quarter == 4 & SD21SE$fleet == "D"] <- "SE, C, Q4, 21"

SD21DK <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD21-DK")
sum(unique(SD21DK$catch_t))
SD21DK$imputation <- NA
SD21DK$imputation[SD21DK$quarter == 2 & SD21DK$fleet == "C"] <- "DK, C, Q2, 20"
SD21DK$imputation[SD21DK$quarter == 2 & SD21DK$fleet == "D"] <- "DK, D, Q1, 21"


c07 <- bind_rows(SD20DE, SD20DK, SD20NO, SD20SE, SD21DK, SD21SE)

rm(SD20DE, SD20DK, SD20NO, SD20SE, SD21DK, SD21SE)

summarise(group_by(subset(c07, wr == "8+"), year, division), ton = sum(catch_t, na.rm = T))
summarise(group_by(c07, year, division), canum = sum(canum, na.rm = T))

```


# 2008
Total CATON and CANUM checked against Thomas figures: CANUM ok, but CATON not the same
Total CATON and CANUM checked against report: ok
Total CATON and CANUM checked against spread sheet: ok
Imputations checked against spread sheet and report if unclear: ok
```{r}
file <- "HER-IIIa-2008new.xls"

sheet_names <- excel_sheets(path = paste0(path_in, file))

SD20NO <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD20-NO")
sum(unique(SD20NO$catch_t))
SD20NO$imputation <- NA
SD20NO$imputation[SD20NO$quarter == 1 & SD20NO$fleet == "C"] <- "DK, C, Q1, 20"
SD20NO$imputation[SD20NO$quarter == 2 & SD20NO$fleet == "C"] <- "DK, C, Q1, 20"
SD20NO$imputation[SD20NO$quarter == 3 & SD20NO$fleet == "C"] <- "DK, C, Q3, 20"
SD20NO$imputation[SD20NO$quarter == 4 & SD20NO$fleet == "C"] <- "DK, C, Q3, 20"

SD20SE <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD20-SE")
sum(unique(SD20SE$catch_t))
SD20SE$imputation[SD20SE$quarter == 1 & SD20SE$fleet == "D"] <- "SE, C, Q1, 20"
SD20SE$imputation[SD20SE$quarter == 2 & SD20SE$fleet == "D"] <- "SE, C, Q2, 20"
SD20SE$imputation[SD20SE$quarter == 3 & SD20SE$fleet == "D"] <- "SE, C, Q3, 20"
SD20SE$imputation[SD20SE$quarter == 4 & SD20SE$fleet == "D"] <- "SE, C, Q4, 20"

SD20DK <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD20-DK")
sum(unique(SD20DK$catch_t))
SD20DK$imputation <- NA
SD20DK$imputation[SD20DK$quarter == 2 & SD20DK$fleet == "C"] <- "DK, C, Q1, 20"
SD20DK$imputation[SD20DK$quarter == 4 & SD20DK$fleet == "C"] <- "DK, C, Q3, 20"
SD20DK$imputation[SD20DK$quarter == 3 & SD20DK$fleet == "D"] <- "DK, D, Q4, 20"

SD20DE <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD20-OTH")
sum(unique(SD20DE$catch_t))
SD20DE$imputation <- NA
SD20DE$imputation[SD20DE$quarter == 2 & SD20DE$fleet == "C"] <- "DK, C, Q1, 20"
SD20DE$imputation[SD20DE$quarter == 3 & SD20DE$fleet == "C"] <- "DK, C, Q3, 20"
SD20DE$imputation[SD20DE$quarter == 4 & SD20DE$fleet == "C"] <- "DK, C, Q3, 20"

SD21SE <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD21-SE")
sum(unique(SD21SE$catch_t))
SD21SE$imputation <- NA
SD21SE$imputation[SD21SE$quarter == 1 & SD21SE$fleet == "D"] <- "SE, C, Q1, 21"
SD21SE$imputation[SD21SE$quarter == 2 & SD21SE$fleet == "D"] <- "SE, C, Q2, 21"
SD21SE$imputation[SD21SE$quarter == 3 & SD21SE$fleet == "D"] <- "SE, C, Q3, 21"
SD21SE$imputation[SD21SE$quarter == 4 & SD21SE$fleet == "D"] <- "SE, C, Q4, 21"

SD21DK <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD21-DK")
sum(unique(SD21DK$catch_t))
SD21DK$imputation <- NA
SD21DK$imputation[SD21DK$quarter == 2 & SD21DK$fleet == "C"] <- "DK, C, Q1, 21"
SD21DK$imputation[SD21DK$quarter == 4 & SD21DK$fleet == "C"] <- "DK, C, Q3, 21"
SD21DK$imputation[SD21DK$quarter == 4 & SD21DK$fleet == "D"] <- "DK, D, Q3, 21"


c08 <- bind_rows(SD20DE, SD20DK, SD20NO, SD20SE, SD21DK, SD21SE)

rm(SD20DE, SD20DK, SD20NO, SD20SE, SD21DK, SD21SE)

summarise(group_by(subset(c08, wr == "8+"), year, division), ton = sum(catch_t, na.rm = T))
summarise(group_by(c08, year, division), canum = sum(canum, na.rm = T))

# Preliminary check against Thomas figures and current time series ok
```


# 2009
Total CATON and CANUM checked against Thomas figures: Kattegat ok. CATON in Skagerrak lower here. CANUM ok
Total CATON and CANUM checked against report: Both figures in Skagerrak a bit higher here
Total CATON and CANUM checked against spread sheet: Both figures in Skagerrak a bit higher here
Imputations checked against spread sheet and report if unclear: Y
```{r}
file <- "HER-IIIa-2009hm.xls"

sheet_names <- excel_sheets(path = paste0(path_in, file))

SD20NO <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD20-NO")
sum(unique(SD20NO$catch_t))
SD20NO$imputation <- NA
SD20NO$imputation[SD20NO$quarter == 1 & SD20NO$fleet == "C"] <- "DK, C, Q2, 20"
SD20NO$imputation[SD20NO$quarter == 2 & SD20NO$fleet == "C"] <- "DK, C, Q2, 20"
SD20NO$imputation[SD20NO$quarter == 3 & SD20NO$fleet == "C"] <- "DK, C, Q3, 20"
SD20NO$imputation[SD20NO$quarter == 4 & SD20NO$fleet == "C"] <- "DK, C, Q4, 20"

SD20SE <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD20-SE")
sum(unique(SD20SE$catch_t))
SD20SE$imputation[SD20SE$quarter == 1 & SD20SE$fleet == "D"] <- "SE, C, Q1, 20"
SD20SE$imputation[SD20SE$quarter == 2 & SD20SE$fleet == "D"] <- "SE, C, Q2, 20"
SD20SE$imputation[SD20SE$quarter == 3 & SD20SE$fleet == "D"] <- "SE, C, Q3, 20"
SD20SE$imputation[SD20SE$quarter == 4 & SD20SE$fleet == "D"] <- "SE, C, Q4, 20"

SD20DK <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD20-DK")
sum(unique(SD20DK$catch_t))
SD20DK$imputation <- NA
SD20DK$imputation[SD20DK$quarter == 1 & SD20DK$fleet == "C"] <- "DK, C, Q2, 20"
SD20DK$imputation[SD20DK$quarter == 1 & SD20DK$fleet == "D"] <- "DK, D, Q2, 20"

SD20DE <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD20-OTH")
sum(unique(SD20DE$catch_t))
SD20DE$imputation <- NA
SD20DE$imputation[SD20DE$quarter == 3 & SD20DE$fleet == "C"] <- "DK, C, Q3, 20"
SD20DE$imputation[SD20DE$quarter == 4 & SD20DE$fleet == "C"] <- "DK, C, Q4, 20"

SD20FO <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD20-OTH (2)")
sum(unique(SD20FO$catch_t))
SD20FO$imputation <- NA
SD20FO$imputation[SD20FO$quarter == 1 & SD20FO$fleet == "C"] <- "DK, C, Q1, 20"


SD21SE <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD21-SE")
sum(unique(SD21SE$catch_t))
SD21SE$imputation <- NA
SD21SE$imputation[SD21SE$quarter == 1 & SD21SE$fleet == "D"] <- "SE, C, Q1, 21"
SD21SE$imputation[SD21SE$quarter == 3 & SD21SE$fleet == "D"] <- "SE, C, Q3, 21"
SD21SE$imputation[SD21SE$quarter == 4 & SD21SE$fleet == "D"] <- "SE, C, Q4, 21"
SD20SE$imputation[SD20SE$quarter == 2 & SD20SE$fleet == "C"] <- "DK, C, Q1, 21"

SD21DK <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD21-DK")
sum(unique(SD21DK$catch_t))
SD21DK$imputation <- NA
SD21DK$imputation[SD21DK$quarter == 2 & SD21DK$fleet == "C"] <- "DK, C, Q1, 21"
SD21DK$imputation[SD21DK$quarter == 3 & SD21DK$fleet == "C"] <- "DK, C, Q4, 21"

SD21DE <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD21-OTH")
sum(unique(SD21DE$catch_t))
SD21DE$imputation <- NA
SD21DE$imputation[SD21DE$quarter == 1 & SD21DE$fleet == "C"] <- "DK, C, Q1, 21"
SD21DE$imputation[SD21DE$quarter == 3 & SD21DE$fleet == "C"] <- "DK, C, Q4, 21"


c09 <- bind_rows(SD20DE, SD20DK, SD20NO, SD20SE, SD20FO, SD21DK, SD21SE, SD21DE)

rm(SD20DE, SD20DK, SD20NO, SD20SE, SD20FO, SD21DK, SD21SE, SD21DE)

summarise(group_by(subset(c09, wr == "8+"), year, division), ton = sum(catch_t, na.rm = T))
summarise(group_by(c09, year, division), canum = sum(canum, na.rm = T))

# Preliminary check against Thomas figures and current time series ok
```


# 2010
Total CATON and CANUM checked against Thomas figures: CANUM ok. CATON not the same
Total CATON and CANUM checked against report: ok
Total CATON and CANUM checked against spread sheet: ok
Imputations checked against spread sheet and report if unclear: ok
```{r}
file <- "HER-IIIa-2010.xls"

sheet_names <- excel_sheets(path = paste0(path_in, file))

SD20NO <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD20-NO")
sum(unique(SD20NO$catch_t))
SD20NO$imputation <- NA
SD20NO$imputation[SD20NO$quarter == 1 & SD20NO$fleet == "C"] <- "DK, C, Q1, 20" 
SD20NO$imputation[SD20NO$quarter == 2 & SD20NO$fleet == "C"] <- "DK, C, Q1, 20"
SD20NO$imputation[SD20NO$quarter == 4 & SD20NO$fleet == "C"] <- "NO, C, Q3, 20"

SD20SE <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD20-SE")
sum(unique(SD20SE$catch_t))

SD20DK <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD20-DK")
sum(unique(SD20DK$catch_t))
SD20DK$imputation <- NA
SD20DK$imputation[SD20DK$quarter == 1 & SD20DK$fleet == "C"] <- "DK, C, Q2, 20"
SD20DK$imputation[SD20DK$quarter == 1 & SD20DK$fleet == "D"] <- "DK, D, Q2, 20"

SD20DE <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD20-OTH")
sum(unique(SD20DE$catch_t))
SD20DE$imputation <- NA

SD20FO <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD20-OTH (2)")
sum(unique(SD20FO$catch_t))
SD20FO$imputation <- NA
SD20FO$imputation[SD20FO$quarter == 4 & SD20FO$fleet == "C"] <- "DK, C, Q4, 20"

SD20LI <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD20-OTH (3)")
sum(unique(SD20LI$catch_t))
SD20LI$imputation <- NA
SD20LI$imputation[SD20LI$quarter == 3 & SD20LI$fleet == "C"] <- "DK, C, Q3, 20"

SD21SE <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD21-SE")
sum(unique(SD21SE$catch_t))
SD21SE$imputation <- NA

SD21DK <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD21-DK")
sum(unique(SD21DK$catch_t))
SD21DK$imputation <- NA
SD21DK$imputation[SD21DK$quarter == 2 & SD21DK$fleet == "C"] <- "DK, C, Q1, 21"

SD21DE <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD21-OTH")
SD21DE$division <- "Kattegat"
sum(unique(SD21DE$catch_t))
SD21DE$imputation <- NA
SD21DE$imputation[SD21DE$quarter == 3 & SD21DE$fleet == "C"] <- "DK, C, Q3, 21"

c10 <- bind_rows(SD20DE, SD20DK, SD20NO, SD20SE, SD20FO, SD20LI, SD21DK, SD21SE, SD21DE)

rm(SD20DE, SD20DK, SD20NO, SD20SE, SD20FO, SD20LI, SD21DK, SD21SE, SD21DE)

summarise(group_by(subset(c10, wr == "8+"), year, division), ton = sum(catch_t, na.rm = T))
summarise(group_by(c10, year, division), canum = sum(canum, na.rm = T))

# Preliminary check against Thomas figures and current time series ok
```

# 2011
Total CATON and CANUM checked against Thomas figures: CANUM ok. CATON different
Total CATON and CANUM checked against report: ok
Total CATON and CANUM checked against spread sheet: ok
Imputations checked against spread sheet and report if unclear: ok
```{r}
file <- "HER-IIIa-2011.xls"

sheet_names <- excel_sheets(path = paste0(path_in, file))

SD20NO <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD20-NO")
sum(unique(SD20NO$catch_t))
SD20NO$imputation <- NA
SD20NO$imputation[SD20NO$quarter == 1 & SD20NO$fleet == "C"] <- "DK, C, Q1, 20"
SD20NO$imputation[SD20NO$quarter == 2 & SD20NO$fleet == "C"] <- "DK, C, Q1, 20"
SD20NO$imputation[SD20NO$quarter == 3 & SD20NO$fleet == "C"] <- "DK, C, Q3, 20"
SD20NO$imputation[SD20NO$quarter == 4 & SD20NO$fleet == "C"] <- "DK, C, Q3, 20"

SD20SE <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD20-SE") # No imputations
sum(unique(SD20SE$catch_t))

SD20DK <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD20-DK")
sum(unique(SD20DK$catch_t))
SD20DK$imputation <- NA
SD20DK$imputation[SD20DK$quarter == 2 & SD20DK$fleet == "C"] <- "DK, C, Q1, 20"
SD20DK$imputation[SD20DK$quarter == 4 & SD20DK$fleet == "C"] <- "DK, C, Q3, 20"
SD20DK$imputation[SD20DK$quarter == 4 & SD20DK$fleet == "D"] <- "DK, D, Q3, 20"

SD20DE <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD20-OTH")
sum(unique(SD20DE$catch_t))
SD20DE$imputation <- NA
SD20DE$imputation[SD20DE$quarter == 4 & SD20DE$fleet == "C"] <- "DK, C, Q3, 20"

SD21SE <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD21-SE")
sum(unique(SD21SE$catch_t))
SD21SE$imputation <- NA

SD21DK <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD21-DK")
sum(unique(SD21DK$catch_t))
SD21DK$imputation <- NA
SD21DK$imputation[SD21DK$quarter == 2 & SD21DK$fleet == "C"] <- "DK, C, Q1, 21"
SD21DK$imputation[SD21DK$quarter == 4 & SD21DK$fleet == "C"] <- "DK, C, Q3, 21"


c11 <- bind_rows(SD20DE, SD20DK, SD20NO, SD20SE, SD21DK, SD21SE)

rm(SD20DE, SD20DK, SD20NO, SD20SE, SD21DK, SD21SE)

summarise(group_by(subset(c11, wr == "8+"), year, division), ton = sum(catch_t, na.rm = T))
summarise(group_by(c11, year, division), canum = sum(canum, na.rm = T))

# Preliminary check against Thomas figures and current time series ok
```

# 2012
Total CATON and CANUM checked against Thomas figures: ok
Total CATON and CANUM checked against report: ok
Total CATON and CANUM checked against spread sheet: ok
Imputations checked against spread sheet and report if unclear: ok
```{r}
file <- "HER-IIIa-2012.xls"

sheet_names <- excel_sheets(path = paste0(path_in, file))

SD20NO <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD20-NO")
sum(unique(SD20NO$catch_t))
SD20NO$imputation[SD20NO$quarter == 1 & SD20NO$fleet == "C"] <- "SE, C, Q1, 20"
SD20NO$imputation[SD20NO$quarter == 2 & SD20NO$fleet == "C"] <- "SE, C, Q2, 20"
SD20NO$imputation[SD20NO$quarter == 3 & SD20NO$fleet == "C"] <- "DK, C, Q3, 20"
SD20NO$imputation[SD20NO$quarter == 4 & SD20NO$fleet == "C"] <- "DK, C, Q4, 20"

SD20SE <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD20-SE") # No imputations
sum(unique(SD20SE$catch_t))

SD20DK <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD20-DK")
sum(unique(SD20DK$catch_t))
SD20DK$imputation <- NA
SD20DK$imputation[SD20DK$quarter == 1 & SD20DK$fleet == "C"] <- "SE, C, Q1, 20"
SD20DK$imputation[SD20DK$quarter == 2 & SD20DK$fleet == "C"] <- "SE, C, Q2, 20"
SD20DK$imputation[SD20DK$quarter == 1 & SD20DK$fleet == "D"] <- "DK, D, Q1, 21"
SD20DK$imputation[SD20DK$quarter == 2 & SD20DK$fleet == "D"] <- "DK, D, Q2, 21"

SD20DE <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD20-OTH")
sum(unique(SD20DE$catch_t))
SD20DE$imputation <- NA
SD20DE$imputation[SD20DE$quarter == 3 & SD20DE$fleet == "C"] <- "DK, C, Q3, 20"
SD20DE$imputation[SD20DE$quarter == 4 & SD20DE$fleet == "C"] <- "DK, C, Q4, 20"

SD21SE <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD21-SE")
sum(unique(SD21SE$catch_t))
SD21SE$imputation <- NA
SD21SE$imputation[SD21SE$quarter == 2 & SD21SE$fleet == "C"] <- "SE, C, Q1, 21"
SD21SE$imputation[SD21SE$quarter == 3 & SD21SE$fleet == "C"] <- "SE, C, Q3, 20"
SD21SE$imputation[SD21SE$quarter == 4 & SD21SE$fleet == "C"] <- "SE, C, Q4, 20"

SD21DK <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD21-DK")
sum(unique(SD21DK$catch_t))
SD21DK$imputation <- NA
SD21DK$imputation[SD21DK$quarter == 1 & SD21DK$fleet == "C"] <- "SE, C, Q1, 21"
SD21DK$imputation[SD21DK$quarter == 2 & SD21DK$fleet == "C"] <- "SE, C, Q1, 21"

c12 <- bind_rows(SD20DE, SD20DK, SD20NO, SD20SE, SD21DK, SD21SE)

rm(SD20DE, SD20DK, SD20NO, SD20SE, SD21DK, SD21SE)

summarise(group_by(subset(c12, wr == "8+"), year, division), ton = sum(catch_t, na.rm = T))
summarise(group_by(c12, year, division), canum = sum(canum, na.rm = T))

# Preliminary check against Thomas figures and current time series ok
```

# 2013
Total CATON and CANUM checked against Thomas figures: CANUM ok. CATON not ok
Total CATON and CANUM checked against report: ok
Total CATON and CANUM checked against spread sheet: ok
Imputations checked against spread sheet and report if unclear: ok
```{r}
file <- "HER-IIIa-2013.xls"

sheet_names <- excel_sheets(path = paste0(path_in, file))

SD20NO <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD20-NO")
sum(unique(SD20NO$catch_t))
SD20NO$imputation[SD20NO$quarter == 1 & SD20NO$fleet == "C"] <- "SE, C, Q1, 20"
SD20NO$imputation[SD20NO$quarter == 2 & SD20NO$fleet == "C"] <- "SE, C, Q2, 20"
SD20NO$imputation[SD20NO$quarter == 3 & SD20NO$fleet == "C"] <- "NO, C, Q4, 20"

SD20SE <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD20-SE") # No imputations
sum(unique(SD20SE$catch_t))

SD20DK <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD20-DK")
sum(unique(SD20DK$catch_t))
SD20DK$imputation <- NA
SD20DK$imputation[SD20DK$quarter == 1 & SD20DK$fleet == "C"] <- "SE, C, Q1, 20"
SD20DK$imputation[SD20DK$quarter == 2 & SD20DK$fleet == "C"] <- "SE, C, Q1, 20"
SD20DK$imputation[SD20DK$quarter == 1 & SD20DK$fleet == "D"] <- "DK, D, Q1, 21"
SD20DK$imputation[SD20DK$quarter == 2 & SD20DK$fleet == "D"] <- "DK, D, Q2, 21"
SD20DK$imputation[SD20DK$quarter == 4 & SD20DK$fleet == "D"] <- "DK, D, Q3, 20"

SD20DE <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD20-OTH")
sum(unique(SD20DE$catch_t))
SD20DE$imputation <- NA
SD20DE$imputation[SD20DE$quarter == 3 & SD20DE$fleet == "C"] <- "DK, C, Q3, 20"
SD20DE$imputation[SD20DE$quarter == 4 & SD20DE$fleet == "C"] <- "DK, C, Q3, 20"

SD21SE <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD21-SE")
sum(unique(SD21SE$catch_t))
SD21SE$imputation <- NA
SD21SE$imputation[SD21SE$quarter == 2 & SD21SE$fleet == "C"] <- "SE, C, Q1, 21"
SD21SE$imputation[SD21SE$quarter == 3 & SD21SE$fleet == "C"] <- "SE, C, Q4, 21"

SD21DK <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD21-DK")
sum(unique(SD21DK$catch_t))
SD21DK$imputation <- NA
SD21DK$imputation[SD21DK$quarter == 1 & SD21DK$fleet == "C"] <- "SE, C, Q1, 21"
SD21DK$imputation[SD21DK$quarter == 2 & SD21DK$fleet == "C"] <- "SE, C, Q1, 21"
SD21DK$imputation[SD21DK$quarter == 3 & SD21DK$fleet == "C"] <- "DK, C, Q3, 20"
SD21DK$imputation[SD21DK$quarter == 4 & SD21DK$fleet == "C"] <- "DK, C, Q4, 20"
SD21DK$imputation[SD21DK$quarter == 3 & SD21DK$fleet == "D"] <- "DK, D, Q3, 20"
SD21DK$imputation[SD21DK$quarter == 4 & SD21DK$fleet == "D"] <- "DK, D, Q3, 20"

c13 <- bind_rows(SD20DE, SD20DK, SD20NO, SD20SE, SD21DK, SD21SE)

rm(SD20DE, SD20DK, SD20NO, SD20SE, SD21DK, SD21SE)

summarise(group_by(subset(c13, wr == "8+"), year, division), ton = sum(catch_t, na.rm = T))
summarise(group_by(c13, year, division), canum = sum(canum, na.rm = T))

# Preliminary check against Thomas figures and current time series ok
```

# 2014
Total CATON and CANUM checked against Thomas figures: CANUM ok. CATON not the same
Total CATON and CANUM checked against report: ok
Total CATON and CANUM checked against spread sheet: ok
Imputations checked against spread sheet and report if unclear: ok
```{r}
file <- "HER-IIIa-2014.xls"

sheet_names <- excel_sheets(path = paste0(path_in, file))

SD20NO <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD20-NO")
sum(unique(SD20NO$catch_t))
SD20NO$imputation[SD20NO$quarter == 1 & SD20NO$fleet == "C"] <- "NO, C, Q2, 20"
SD20NO$imputation[SD20NO$quarter == 3 & SD20NO$fleet == "C"] <- "DK, C, Q3, 20"
SD20NO$imputation[SD20NO$quarter == 4 & SD20NO$fleet == "C"] <- "DK, C, Q3, 20"

SD20SE <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD20-SE") # No imputations
sum(unique(SD20SE$catch_t))

SD20DK <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD20-DK")
sum(unique(SD20DK$catch_t))
SD20DK$imputation <- NA
SD20DK$imputation[SD20DK$quarter == 2 & SD20DK$fleet == "C"] <- "DK, C, Q1, 21"
SD20DK$imputation[SD20DK$quarter == 2 & SD20DK$fleet == "D"] <- "DK, D, Q2, 21"
SD20DK$imputation[SD20DK$quarter == 4 & SD20DK$fleet == "D"] <- "DK, D, Q3, 20"

SD20DE <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD20-OTH")
sum(unique(SD20DE$catch_t))
SD20DE$imputation <- NA
SD20DE$imputation[SD20DE$quarter == 4 & SD20DE$fleet == "C"] <- "DK, C, Q4, 20"

SD20FO <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD20-OTH (2)")
sum(unique(SD20FO$catch_t))
SD20FO$imputation <- NA
SD20FO$imputation[SD20FO$quarter == 3 & SD20FO$fleet == "C"] <- "DK, C, Q3, 20"

SD21SE <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD21-SE")
sum(unique(SD21SE$catch_t))
SD21SE$imputation <- NA # No imputations

SD21DK <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD21-DK")
sum(unique(SD21DK$catch_t))
SD21DK$imputation <- NA
SD21DK$imputation[SD21DK$quarter == 2 & SD21DK$fleet == "C"] <- "DK, C, Q1, 21"
SD21DK$imputation[SD21DK$quarter == 3 & SD21DK$fleet == "C"] <- "DK, C, Q3, 20"
SD21DK$imputation[SD21DK$quarter == 4 & SD21DK$fleet == "C"] <- "DK, C, Q3, 20"

c14 <- bind_rows(SD20DE, SD20DK, SD20NO, SD20SE, SD20FO, SD21DK, SD21SE)

rm(SD20DE, SD20DK, SD20NO, SD20SE, SD20FO, SD21DK, SD21SE)

summarise(group_by(subset(c14, wr == "8+"), year, division), ton = sum(catch_t, na.rm = T))
summarise(group_by(c14, year, division), canum = sum(canum, na.rm = T))

# Preliminary check against Thomas figures and current time series ok
```

# 2015
Total CATON and CANUM checked against Thomas figures: CANUM ok. CATON not the same
Total CATON and CANUM checked against report: ok
Total CATON and CANUM checked against spread sheet: ok
Imputations checked against spread sheet and report if unclear: ok
```{r}
file <- "HER-IIIa-2015.xls"

sheet_names <- excel_sheets(path = paste0(path_in, file))

SD20NO <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD20-NO")
sum(unique(SD20NO$catch_t))
SD20NO$imputation <- NA
SD20NO$imputation[SD20NO$quarter == 1 & SD20NO$fleet == "C"] <- "SE, C, Q1, 20"
SD20NO$imputation[SD20NO$quarter == 2 & SD20NO$fleet == "C"] <- "SE, C, Q1, 20"
SD20NO$imputation[SD20NO$quarter == 3 & SD20NO$fleet == "C"] <- "DK, C, Q3, 20"
SD20NO$imputation[SD20NO$quarter == 4 & SD20NO$fleet == "C"] <- "SE, C, Q4, 20"

SD20SE <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD20-SE") # No imputations
sum(unique(SD20SE$catch_t))
SD20SE$imputation <- NA
SD20SE$imputation[SD20SE$quarter == 2 & SD20SE$fleet == "C"] <- "SE, C, Q1, 20"

SD20DK <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD20-DK")
sum(unique(SD20DK$catch_t))
SD20DK$imputation <- NA
SD20DK$imputation[SD20DK$quarter == 2 & SD20DK$fleet == "C"] <- "SE, C, Q1, 20"
SD20DK$imputation[SD20DK$quarter == 1 & SD20DK$fleet == "D"] <- "DK, D, Q1, 21"
SD20DK$imputation[SD20DK$quarter == 2 & SD20DK$fleet == "D"] <- "DK, D, Q2, 21"

SD20DE <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD20-OTH")
sum(unique(SD20DE$catch_t))
SD20DE$imputation <- NA
SD20DE$imputation[SD20DE$quarter == 4 & SD20DE$fleet == "C"] <- "SE, C, Q4, 20"

SD20FO <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD20-OTH (2)")
sum(unique(SD20FO$catch_t))
SD20FO$imputation <- NA
SD20FO$imputation[SD20FO$quarter == 1 & SD20FO$fleet == "C"] <- "SE, C, Q1, 20"

SD20NL <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD20-OTH (3)")
sum(unique(SD20NL$catch_t))
SD20NL$imputation <- NA
SD20NL$imputation[SD20NL$quarter == 3 & SD20NL$fleet == "C"] <- "DK, C, Q3, 20"

SD21SE <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD21-SE")
sum(unique(SD21SE$catch_t))
SD21SE$imputation <- NA 
SD21SE$imputation[SD21SE$quarter == 3 & SD21SE$fleet == "C"] <- "SE, C, Q4, 21"

SD21DK <- read_canum_sheet_old_format_IIIa(file = paste0(path_in, file), sheet_name = "SD21-DK")
sum(unique(SD21DK$catch_t))
SD21DK$imputation <- NA
SD21DK$imputation[SD21DK$quarter == 1 & SD21DK$fleet == "C"] <- "SE, C, Q1, 21"
SD21DK$imputation[SD21DK$quarter == 2 & SD21DK$fleet == "C"] <- "SE, C, Q2, 21"

c15 <- bind_rows(SD20DE, SD20DK, SD20NO, SD20SE, SD20FO, SD20NL, SD21DK, SD21SE)

rm(SD20DE, SD20DK, SD20NO, SD20SE, SD20FO, SD20NL, SD21DK, SD21SE)

summarise(group_by(subset(c15, wr == "8+"), year, division), ton = sum(catch_t, na.rm = T))
summarise(group_by(c15, year, division), canum = sum(canum, na.rm = T))

# Preliminary check against Thomas figures and current time series ok
```

# Combine
```{r}

dat <- bind_rows(c00, c01, c02, c03, c04, c05, c06, c07, c08, c09, c10, c11, c12, c13, c14, c15)
rm(c00, c01, c02, c03, c04, c05, c06, c07, c08, c09, c10, c11, c12, c13, c14, c15)
unique(dat$year)
unique(dat$ctry)

# Clean up codes
dat$area <- NA
dat$area[dat$division == "Kattegat"] <- "27.3.a.21"
dat$area[dat$division == "Skagerrak"] <- "27.3.a.20"

dat$ctry[dat$ctry == "DK"] <- "Denmark"
dat$ctry[dat$ctry == "Faroee"] <- "Faroe Islands"
dat$ctry[dat$ctry == "NLD"] <- "Nedtherlands"

dat$canum_1000 <- dat$canum
dat$weca_g <- dat$weca
```

# Output
```{r}

write.table(dat, "../data/canum_old_format_3a.csv", row.names = F, sep = ";")

```

